### 2023-07-30 paper/paper.tex
add sql figures paper

\documentclass{article}

\usepackage{graphicx}
\graphicspath{ {../figures/} }

\title{An Exploration of Analysis Methods on Predictive Models of Student Success}
\author{Alex Beckwith\\\\University of New Hampshire}
\date{May 2023}
\begin{document}

\maketitle
\newpage

\tableofcontents

\begin{abstract}
    Machine learning models are not always evaluated with statistical rigor. 
    This can lead to inferential flaws when assumptions are made about the underlying and performance data, especially when cross-validation is used. 
    In this paper, a Bayesian method of model evaluation is compared to a non-parametric frequentist method. 
    In addition, a metric for analyzing the fairness of a particular algorithm is tested.

    The evaluation techniques were applied to a dataset of student and course data made available by the Open University. 
    A system was built to train and test predictive models of student success. 
    The aim was to predict students at risk of failing or withdrawing from a course using the first 30 days of data extracted from the virtual learning environment. 
    In an applied setting, these predictions could be used to direct additional resources to at-risk students.

    The project included creating a database to cleanse, transform, and analyze the dataset. 
    Features were engineered to use as predictive inputs using a combination of exploratory analysis and inspiration from research. 
    Four different subsets of input features were applied to nine different classification algorithms. 
    Both randomized and exhaustive hyperparameter tuning procedures were experimented with, which created hundreds of distinct hyperparameter settings.

    The Bayesian strategy provided more conclusive results by determining a “region of practical equivalence” as opposed to an inability to reject the null hypothesis. 
    The results were similar to findings from research, which typically found tree-based ensemble methods in the upper-equivalence region.

    The proposed metric for predictive fairness is called the Absolute Between Receiver Operating Characteristic Area (ABROCA). 
    This metric was first introduced at the 2019 International Learning Analytics and Knowledge Conference. 
    A significant relationship between ABROCA and the gender ratio of a course as well as between ABROCA and the ratio of students in a course identifying as having a disability. 
    No significant relationship was found between ABROCA and overall model performance. 
\end{abstract}
\newpage

\section{Introduction}
        When creating a predictive model to solve a problem, many different formulations and algorithms are typically tested.
        Datasets can be vast and complex, so the "see what sticks" strategy is often a good first step.

        Selecting the approriate model to deploy should involve the consideration of many factors.
        Predictive performance is important, but simply picking the model with the highest mean accuracy is not a valid strategy.
        Statistical evaluation enables confident decisionmaking, which frees the researcher to address other considerations.

        In this project, I applied the best practices from my research on model evaluation to a publicly-available dataset provided by an educational institution.
        I created a system that generates models that attempt to predict students who are likely to fail or drop out of a course.
        The practical application of the final model's predictions would be to target vulnerable students with interventions to increase their likelihood of course completion.

        Using the results of the model testing, I show why a Bayesian approach is better for the evaluation of predictive models. 
        In addition, I implement a new metric for testing model fairness. 
        I affirm the results of the researchers who proposed the metric, showing that it is strongly correlated with a decrease in predictive fairness while showing scant correlation with predictive performance.

    \subsection{Research Questions}
        \begin{enumerate}
            \item Which models and featuresets are best at predicting student outcomes?
            \item How do the results differ when evaluated using naive, frequentist, and Bayesian procedures?
            \item Is there an association between model predictive performance and Absolute Between Receiver Operating Characteristic Area (ABROCA)?
        \end{enumerate}

\section{Previous Research}
    \subsection{Learning Analytics}
        This project falls squarely within the interdiciplinary field of Educational Data Science (EDS), which itself is the union of Learning Analytics (LA) and Educational Data Mining (EDM).
        EDM is primarily concerned with the development of methods for exploring the unique types of data that come from education environments \cite{educate2019}.
        LA is focused on the analysis of learners and the optimization of the learning process \cite{educate2019}.
        The first EDM and LA-specific conferences took place in 2008 and 2011, respectively. 
        All three have roots in statistics, education, and computer science, and all three use data to address important educational questions and issues.
        For a more comprehensive review of these fields, please refer to \cite{educate2007,educate2010,educate2019}.

    \subsection{Modeling Student Performance}
        \subsubsection{Predictions}
            One of the most common topics in LA and EDM is the creation of machine learning models to predict student behavior and performance.
            Researchers most often frame problems in the context of classification and regression problems \cite{educate2007,educate2010,educate2019}.
            Within the subset of research on classification and regression models, the most common features to predict were outcomes and scores \cite{compare2015}.
            In the context of a course, that might be whether the student passes or their final grade.
            One could also consider the context of a single problem, such as the student's most likely answer or the probability of being correct/incorrect \cite{explore2021}.
            The most effective algorithms for classification problems of these type in my research were tree-based ensemble methods.

        \subsubsection{Model Types}
            In my research, the models which best predicted student performance tended to be tree-based ensemble methods \cite{explore2021,engage2014,assign2021esteban}.
            Tree-based methods were also the most commonly seen type of model, followed by linear and logistic regression \cite{assign2021esteban}.
            Other common models include support vector machines, k-nearest neighbors, and naive Bayes.
            Research related to the utilization of deep learning is not uncommon \cite{explore2021,assign2021esteban}, though I wasn't able to find a resource which utilized a neural network that significantly outperformed simpler methods.

    \subsection{Student Data}
        \subsubsection{Sources}
            The most common sources of student data came from Massively Open Online Courses (MOOCs), Intelligent Tutoring Systems (ITS) and other computer-based platforms,
            though a great deal of research has also been conducted using data from traditional classrooms \cite{educate2019,early2021,assign2021esteban,explore2015}.
            Especially since the pandemic of the early 2020s, many students have experienced educational systems which blend the two.
            Blended sources of learning data would benefit from additional research \cite{educate2019,early2021}.

        \subsubsection{Featuresets}
            The most common featuresets for predicting student outcomes are are academic, demographic, and behavioral \cite{engage2014,eval2018,early2019,assign2021esteban,compare2015}.
            Academic includes information about assessments and assignments \cite{assign2021esteban}.
            Behavioral data is often the logs from student interactions with the Virtual Learning Environment (VLE) \cite{early2019,assign2021esteban}.
            Some research also includes biometric and visual data, such as a student's heartbeat and facial expression as they work through a problem \cite{assign2021chango}.

        \subsubsection{Feature Extraction Strategies}
            I found three categories of sources that were utilized in research, all with distinct benefits and compromises \cite{automl2021,towards2014}.
            Some researches utilize an automated system to extract features.

            In \cite{automl2021}, two automated feature-engineering systems were compared against a set of results produced by experts in EDM.
            One of the systems outperformed the other two sets, but at the risk of being significantly less interpertable.
            In many cases, the ability to explain why a particular feature is predictive of a result is paramount to producing actionable conclusions from the experiment.
            Another source suggested that the crowdsourcing of features in addition to exploration and expert recommendation produced useful results \cite{towards2014}.

    \subsection{Model Evaluation Methods}
        \subsubsection{Naive Averaging}
            Naive averaging is the evaluation tactic by which models are evaluated by ranking by the average of the target metric between runs an that alone. 
            This strategy is both common and problemtatic because it doesn't take into account the magnitude and variability of differences in performance \cite{eval2018}.

        \subsubsection{Frequentist}
            Null-hypothesis significance testing (NHST) is a common tool for differentiating the results of experiments.
            While useful to many problems, evaluating predictive models using NHST does not produce satisfying, actionable result.
            The t-test is a popular test to compare groups of returned values. 
            Because most machine learning models utilize cross validation, the t-test is invalidated.
            One typically wants to be able to conclusively say which model is better on a variety of metrics in order to deploy said model.
            The result of NHST is either the rejecting of the null hypothesis or an inability to reject the null hypothesis.
            Typically involves running a global test for grouped mean differences, followed by a pairwise comparison test pending the results of the global test.
            In my research, the recommended NHST strategy was to use non-parametric tests as they work without working on the assumption that the means are normally distributed. 
            Therefore, the recommended global test was a Friedman test for the global test and a Nemenyi test for pairwise differences.

        \subsubsection{Bayesian}
            The recommended approach to compare classification models is Bayesian in nature \cite{eval2018,stat2017,time2017}.
            Similar to the frequentist approach, pairwise differences are compared using a test.
            The primary difference between the output of these strategies is that the Bayesian test can produce what might be considered a "three-tailed" test.
            That is, there are three regions produced by the modelled probability density function (PDF).
            There's the probability that either model is better to a significantly discernable degree.
            In addition, there's the Region Of Practical Equivalence (ROPE), the probability that for all practical purposes, the two models produce equivalent results.
            The ROPE is specified as the difference in proportion between the two models being compared. 
            For example, a ROPE value of 0.01 is assessing the probability that the mean of the two classifiers' results will be within 1 percent.
            eg for all practical purposes, they can be considered equivalent. 
            Another benefit of the Bayesian method is its robustness to multiple comparisons and  its accounting for cross-validation.
            \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{rope_rforest_519_0__etree_358_0_.png}
                \caption{A probability density function resulting from a Bayesian Signed Rank Test}
                \label{fig:bayes_on_one}
            \end{figure}
            \newline
            \begin{figure}
                \centering
                    \includegraphics[width=0.5\textwidth]{rope_on_two_hxg_boost_531_0__hxg_boost_540_0_.png}
                    \caption{A Bayesian posterior plot resulting from a Bayesian hierarchical correlated t-test}
                    \label{fig:bayes_on_two}
                \end{figure}
                \newline
                The package baycomp \cite{baycomp} is a Python package that implements these Bayesian tests.
                It uses hierarchical for multiple datasets, signed rank for single. 
                The package appears to have been created and refined while this paper was being written \cite{stat2017}

                \subsubsection{ABROCA | Slicing Analysis}

                To understand ABROCA, it is necessary to understand the Receiver Operating Characteristic (ROC).
                The ROC is a function of the false positive rate to true positive rate over the range of threshold values for a predictor.
                originally used to measure performance of radar equipment
                For a more formal exploration of the mathematical properties of the ROC, see \cite{roc2014}.

                By integrating over the range of threshold values $[0, 1]$, one finds the area under ROC curve (ROC AUC), a commonly used as a metric to optimize performance of machine learning models.
                By maximizing the ROC AUC, one is maximizing the density of correct predictions while making the threshold value arbitrary.
                It follows that a perfect predictor would reach the theoretical maximum of ROC AUC $= 1.0$, having correct prediction at all threshold values.
                The lowest practical ROC AUC is that of a random predictor, ROC AUC = 0.5. In this case, the model is equally likely to pick correctly or incorrectly at all threshold values.

                ABROCA is a metric used to analyze model fairness.
                It was first introduced at 2019 International Learning Analytics and Knowledge Conference \cite{eval2019}.
                To calculate ABROCA, split dataset by feature of interest and obtain the ROC for the model's predictions on each partion of the split dataset.
                Sum absolute values of between-curve area.

                How does this relate to fairness?
                A model that produces equivalent prediction probabilities for the subgroups of the split dataset equally would have ABROCA = 0. 
                Producing the same prediction probabilities wouldproduce the same ROC curves, so there would be no area to sum.
                Hypothesis - Higher ABROCA associated with lower predictive fairness
                \cite{eval2019} found significant differences in fairness when testing different models on a large collection of Massively Open Online Course (MOOC) datasets.
                \begin{enumerate}
                    \item Significant Differences
                    \begin{enumerate}
                        \item Statistical Algorithm
                        \item Featureset Used
                    \end{enumerate}
                    \item Relationship to ABROCA
                    \begin{enumerate}
                        \item Gender Imbalance Ratio
                        \item Curricular Area
                    \end{enumerate}
                    \item Specific Course
                    \begin{enumerate}
                        \item Performance and Fairness
                        \item Not a strict tradeoff with performance and fairness
                    \end{enumerate}
                \end{enumerate}

\section{Experimental Architecture}
    \subsection{Dataset}
        \subsubsection{Background}
            The dataset I used in this experiment was made public by the Open University (OU), an online institution based in the United Kingdom.
            The OU provisions one of the largest publicly available LA datasets, known as the Open University Learning Analytics Dataset (OULAD) \cite{oulad}.
            The data comes from 23 presentations (semesters) of 7 different Massive Open Online Courses (MOOCs) (called "modules" by the university) over 2 years and includes demographic, assessment, Virtual Learning Environment (VLE), and course information.
            VLE data is summarized by the number of clicks per course activity per student per day, which amounts to 10,655,280 records associated with 32,593 students.
            In order to be included in the OULAD, a module-presentation had to have over 500 students, at least two different presentations, and utilize the VLE.
            The module also had to have a significant amount of failing students.

            \begin{figure}
                \includegraphics[width=0.5\textwidth]{oulad_students_courses}
                \caption{Module summary and domain information \cite{oulad}}
                \label{fig:oulad_students_courses}
            \end{figure}

        \subsubsection{Description of Tables}

            The Open University Learning Analytics Dataset (OULAD) consists of seven tables.
            One table contains student demographic information. 
            A trio of tables describe the courses. 
            There's a table containing the distinct module and presentation codes and a table each for the assessments and Virtual Learning Environment (VLE) activities for each course.
            The three remaining tables bridge the student demographic table with each of the course tables. 
            One table contains the inforamiton about course registration.
            One summarizes students' interactions with individual VLE activities on a daily timescale.
            One contains records on students' assessment completion.

            \begin{figure}
                \centering
                \includegraphics[width=0.75\textwidth]{raw_model}
                \caption{An entity-relationship diagram describing the published dataset \cite{oulad}.}
                \label{fig:oulad_schema}
            \end{figure}

        \subsubsection{Comparison to 2015 Data}
            The publishers of the dataset performed an analysis on the distribution of demographic characteristics over time.
            Specifically, they compared a sample of student data from 2015 to the dataset distributions of module CCC, which are from 2013 and 2014.
            The authors performed chi-squared and Wilcox tests to evaluate the null hypothesis that the mean values of these distributions are equivalent.
            At typical significance levels, the null hypothesis cannot be rejected.

            \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{oulad_vs_15}
                \caption{Evaluation of similarity between OULAD and 2015 data for CCC module \cite{oulad}.}
                \label{fig:oulad_vs_15}
            \end{figure}

            A difference between the data from the authors' analysis and the published dataset is the granularity of the information available.
            An anonymization tool was used to obfuscate identifying details in the data while still including specific student demographic information. 
            To illustrate the impact on the data, please see figure xyz.
            \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{oulad_15_age}
                \caption{The distribution of student ages for OULAD data (blue) and 2015 data (red) for CCC module \cite{oulad}.}
                \label{fig:oulad_15_age}
            \end{figure}
            \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{age_band_by_student}
                \caption{The distribution of published OULAD age groups \cite{oulad}.}
                \label{fig:age_band_by_student}
            \end{figure}

            \subsubsection{Other Student Characteristics}

            \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{final_result_by_student}
                \caption{The distribution of published OULAD final module results. \cite{oulad}.}
                \label{fig:final_result_by_student}
            \end{figure}
            \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{region_by_student}
                \caption{The distribution of published OULAD final module results. \cite{oulad}.}
                \label{fig:region_by_student}
            \end{figure}

        \subsection{Feature Extraction}

            \subsubsection{Database System}
                I chose to create a PostgreSQL relational database to organize the cleansing pipeline for this project \cite{postrgesql}.
                PostgreSQL is an open source, performant, and reliable relational database system. 
                The clear syntax of Structured Query Language (SQL) for scripting transformations 
                and database operations enabled me to wrangle millions of rows efficiently.

            \subsubsection{Flat Files to Main}
                The first step in utilizing the database was injesting the data.
                I used the Python package pandas to load the Comma-Separated Values (CSV) files into a schema called [landing].
                I then created a schema called [staging] and used SQL to correct and optimize the datatypes of the landing tables.       
                I created a schema called [main] to hold an alternative structure of the data.
                \newline
                The categorical text fields from the staging tables were each given a table to store their distinct values with an integer id as a primary key.
                In the original tables, distinct courses required two text fields for identification.
                In the original student table, the same two fields were necessary, with the addition of an integer student\_id. 
                During the process of transforming the tables into [main], I created a [course\_id] field to identify each module/presentation combination with a single integer.
                I also created a [student\_id] field to identify each individual student record with a distinct integer. 
                Using a single integer field instead of multiple text fields to identify distinct records leads to significant efficiency improvements in storage, memory, and computation.
                While creating new [student\_info] and [course\_info] tables in the [main] schema, I used the new categorical tables to substitute the text values for integer ids.
                This was advantageous not only for the efficiency of utilizing the database, but also because some machine learning models only accept numeric values as input.

            \subsubsection{Main to First30}
                A great deal of research exists which utilizes predictive modeling to enhance the learning experience.
                This information could be used to intervene positively impact students' lives, increasing graduation rates.
                For my project, I decided to predict course outcome.
                This information is most useful when it can be predicted early, which is why I limited the data used for predictions to the first 30 days from the start of the course.
                I also excluded data relating to students who dropped out before the 30 day mark so that their lack of data for certain features wouldn't impact the training process.
                \newline
                I therefore decided to 
                Difference in proportion from Main to First30 for 
                Shown demographics
                Final Outcomes
                LAnding to Main Database schema decisions
                Main to First30 Database schema decisions

            \subsubsection{Feature Engineering}
                I built features to use as inputs for the predictive models with inspiration from research and by following intuition \cite{automl2021, early2019}.
                The breadth of feature extraction strategies in research spanned from subject-matter expertise to automation and crowdsources, all of which have their merits.

                Some of the features were built in, requiring only the effort to collect to utilize, such as gender and region.
                The major categories of features fall into these four groups: student demographic information, course information, assessment data, and VLE interaction data. 
                The assessment and interaction categories are where most of the "derived" features sit.

                Here's an example of a feature in the VLE activity category that I created when following intuition:
                \begin{figure}
                    \centering
                    \includegraphics[width=1\textwidth]{n_days_active}
                    \caption{The number of distinct days that students interacted with the VLE in the first 30 days}
                    \label{fig:n_days_active}
                \end{figure}

                Here's an example of a feature in the VLE activity category that I built based on on of the expert-created fields in this paper \cite{automl2021}:
                \begin{figure}
                    \centering
                    \includegraphics[width=1\textwidth]{n_total_clicks_by_top_5th_clicks}
                    \caption{The total number of clicks on activities ranked in the top 5th percentile of activities as measured by student clicks}
                    \label{fig:n_total_clicks_by_top_5th_clicks}
                \end{figure}

        \subsection{Algorithms and Hyperparameters}
            Hyperparameters are the input parameters for the operation of a machine learning model.
            All of the algortihms and parameter selection components I used are part the Python package scikit-learn \cite{sklearn}
            \subsubsection{Hyperparameter Selection}
                I utlized two different strategies for parameter selection: GridSearch and RandomSearch.
                GridSearch is a brute force strategy where one can specify collections of parameter selections and the cross-validating object will walk through them all. 
                RandomSearch is similar to GridSearch in the way that parameters are mapped out, but selects random combinations from the available ranges.
                Interestingly, one can even set scipy \cite{scipy} random variables as distributions for this cross-validation strategy to pick from during testing.

                My logic for using both strategies was to first apply wide ranges of parameter combinations for the GridSearch strategy.
                I then used the results from runs to restrict the parameter ranges to those yielding better results.
                Better results in this case refers to higher average ROC AUC while also running in a reasonable timespan. 
                If models were taking longer than 30 minutes to run, I moved the limits of the parameter selection ranges to avoid that when possible.
                The optimization algorithms used to train these models can sometimes not converge to a local (ideally global) minimum, meaning that the predictions will not be the ebst, which is why restricting the paramter ranges is necessary.

                Once the paramter ranges were sufficiently restricted, I ran my model-generating pipeline using the RandomSearch strategy.
                This can be advantegous because certain combinations of parameter values will never be tried on a reasonable timescale while using a brute force strategy.

            \subsubsection{Algorithms}
                Here is a list of the classification algorithms used in this project along with abbreviations that will appear in later figures. 
                If curious about a particular model or its available parameters, please see \cite{sklearn}.
                The parameterizations of the top two models will be included in the results section of this paper.
                \begin{itemize}
                    \item Decision Tree
                    \item Ada Boosting with decision tree as submodel
                    \item Histogram Gradient Boosting
                    \item Random Forest
                    \item Extra Trees
                    \item K-Nearest Neighbors
                    \item Logistic Regression
                    \item Multi-Layer Perceptron
                    \item Support Vector Machines
                \end{itemize}

        \subsection{Model Pipeline}
            The model generating, training, and testing pipeline was created using scikit-learn components \cite{sklearn} 
            I created separate Python classes that worked together to handle the feature selection, data preprocessing, and parameter selection.
            A class I called ModelEngine orchestrated the process from generation to the logging of results.

            \subsubsection{Data Preprocessing}
                In the data preprocessing pipeline, features were transformed in order to improve their compatability with making predictions.
                Categorical data was encoded using the "one hot" strategy where each value was pivoted into a Boolean feature.    
                All Boolean features were made numeric.
                Once all features are numeric, the pipeline standardizes each field so that the mean is zero and the variance is one.
                This improves the algorithm's predictive performance by not allowing any of the features to artificially outweigh any other.

                If values were missing or null, they were imputed as zeros.
                I decided to impute them instead of exclude them in order to conserve as much data as possible for training.

                Any fields with zero-variance are excluded in order to increase computational efficiency.
                With no variance, a field won't be predictive of any result, and will instead just add overhead.
                Another strategy implemented to increase efficiency is Principle Component Analysis (PCA) using a Maximum-Likelihood Estimator (MLE) strategy.
                Similar to the variance threshold, PCA works by reducing model dimensionality in orer to reduce model training time, though through a more complex process.

            \subsubsection{Model Training}
                Each model was crossvalidated using a repeated stratified k folds algorithm.
                Each run included five splits and two repeats, totalling ten runs for each model parameterization.
                During training, each model was refit by attempting to maximize ROC AUC.
                The feature that was predicted for the experiment was is\_withdrawn\_or\_fail, simple binary classification.
                The training and testing proportions varied between 0.25 and 0.35.

\section{Results Analysis}
    \subsection{Naive Averaging}
            By simply averaging the results and sorting by performance, we'd miss key details.
            In the below figure, we can see that there is quite a degree of variability on key metrics like predictive performance and fit time.
        \begin{figure}
            \centering
            \includegraphics[width=1\textwidth]{roc_fit_by_mtype}
            \caption{The mean and standard deviation of fit time and ROC AUC by model type}
            \label{fig:roc_fit_by_mtype}
        \end{figure}

    \subsection{Null Hypothesis Significance Testing}
        For the frequentist model comparison, I used non-parametric tests to evaluate model differences.
        I wanted to make as few assumptions as possible about the distribution of the underlying data.
        Additionally, since cross-validation was used, we shouldn't use a ttest \cite{why2009, eval2018}.

        A Friedman test \cite{scipy, eval2018} to check for global differences returned a p-value of less than 10e-6, so I turned to the Nemenyi signed rank test \cite{scipy, eval2018} to look at pairwise differences.
        The results can be seen on the below figure, which illustrate one of the major pitfalls of utilizing frequentist methods for model evaluation.
        The wide band of gray shows where we have an inability to reject the null hypothesis at a significance level of 0.05 for the top 69 models.
        That the performance of the models is approximately equivalent is not particularly conclusive.

        \begin{figure}
            \centering
            \includegraphics[width=0.95\linewidth]{freq_window_20_16_top_100.png}
            \caption{A windowpane plot showing the results of the non-parametric Nemenyi test}
            \label{fig:freq_window_20_16_top_100}
        \end{figure}

    \subsection{Bayesian Region of Practical Equivalence}
        When evaluating model performance using the Bayesian strategy, we find much more conclusive results.
        A Bayesian signed rank test \cite{stat2017, eval2018, time2017} was used to evaluate each pairwise comparison using a ROPE of 0.002.
        I attempted to do all pairwise comparisons with full hierarchical model tests, but the computational overhead for the number of comparisons was too high.

        The same top 100 results are shown, but with only two models in the uppermost ROPE, an Extra Tree and a Random Forest model.
        Even looking at the top two approximately-equivalent regions, the top six of seven are tree-based ensemble methods, similar to research.
        Surprisingly there ain't an Ada Boostingup there.

        \begin{figure}
            \centering
            \includegraphics[width=0.95\linewidth]{bayes_window_20_16_top_100.png}
            \caption{A windowpane plot showing the results of a Bayesian signed rank test using a ROPE of 0.002}
            \label{fig:bayes_window_20_16_top_100}
        \end{figure}

    \subsection{Fairness Though Slicing Analysis}
        I also evaluated the ABROCA statistic and found similar results to \cite{eval2019}.

        First, we have a visualization of two models, each being split two ways.
        In both cases, the extra tree model appears to have better average predictive performance than the logistic regression.
        Both models have a similar ABROCA when it comes to predictions for disabled students, but the extra tree model appears to make predictions less fairly when it comes to gender.

        \begin{figure}
            \centering
            \includegraphics[width=1\textwidth]{abroca_logreg_271_0_etree_358_0_.png}
            \caption{The ABROCA statistic for two models split by is\_female and has\_disability}
            \label{fig:abroca_logreg_271_0_etree_358_0_}
        \end{figure}

        The top four models happened to be different model types, so I retrained and evaluated the ABROCA for each model on each distict course's data.
        The points on each chart represent an individual model's ABROCA score for an individual course, differentiate by color for each course domain. 
        The top two plots show two quadratic regressions that seem to indicate a strong correlation between ABROCA and both the course disabled ratio and course female ratio.
        The bottom two plots appear to show a rather weak correlation between the models' predictive performance and ABROCA.

        \begin{figure}
            \centering
            \includegraphics[width=1\textwidth]{abroca_by_gender_dis}
            \caption{The relationship between ABROCA and demographic balance and mean test ROC AUC for the top four models}
            \label{fig:abroca_by_gender_dis}
        \end{figure}

\section{Conclusion}

    \subsection{Best Models and Features}
        In this experiment, I found that tree-based ensemble methods tended to be the best-performing models on this dataset, with these features.
        The models which performed the best were those that used the entire set of features, not just a subset.

    \subsection{Best Evaluation Method}
        Similar to expectations, we found that Bayesian evaluation methods produced the most conclusive answer to the "which model is better question" and suffers from the fewest assumptions or invalidations.

    \subsection{Fairness vs Performance}
        We did not see a strong relationship between model predictive performance (as measured by ROC AUC) and ABROCA.
        There did appear to be a strong relationhip between demographic ratio and ABROCA.
        This result seems to indicate the ABROCA may be a useful metric in the evaluation of model fairness.
        In addition, this usefulness does not appear to come at the cost of predictive performance.

    \subsection{Future Work}
        To extend this work, additional development of the model generation system could allow for automated hyperparameter distribution optimization.
        More time could be spent refining the feature database and extracting additional predictive features.
        Expend more computing resources on hierarchical comparisons rather than different parameterizations

        A future researcher might evaluate the ABROCA statistic on additional datasets and different categorical splits.
        An attempt could be made to integrate it into the model selection process.
        One might explore if a higher-dimension expression of the calculation holds water (get it, volume).
        More of the mathetmatical properties of ABROCA could be explored.

        \bibliographystyle{plain}
        \bibliography{paper}
    \end{document}

### 2023-07-30 src/db_helpers.py
refactor with flake8

@@ -1,0 +1,517 @@
+# standard library imports
+from math import log, sqrt
+from pathlib import Path
+from os import getenv
+from subprocess import Popen, PIPE
+from typing import Any
+
+# third party imports
+from matplotlib.pyplot import xticks, subplots
+from numpy.random import choice
+from psycopg2 import connect
+from psycopg2.errors import UndefinedTable, ProgrammingError
+from pandas import read_sql, DataFrame, Series
+from seaborn import histplot
+from sqlalchemy import create_engine
+
+from utils import get_distinct_col_vals, get_props, series_col
+from utils import set_envs, filter_df, pathsearch
+
+set_envs("db")
+
+if getenv("CONTEXT") is None:
+    set_envs("model")
+
+
+def onehot_case(col: str, val: str):
+    return f"case when {col} = '{val}' then 1 else 0 end"
+
+
+def pyth(_list: list):
+    return sqrt(sum([x ** 2 for x in _list]))
+
+
+def get_deets(context: str):
+    context = context.upper()
+    dbname = "DBNAME"
+    vars = ["DBHOST", "DBPORT", "DBSUDO"]
+    deets = [dbname] + [context + x for x in vars]
+    deets = [getenv(x) for x in deets]
+    return deets[0], deets[1], deets[2], deets[3]
+
+
+def create_conn(dbname: str,
+                host: str,
+                port: str,
+                user: bool,
+                pw: str = None
+                ):
+    dbname = f"dbname={dbname}"
+    host = f"host={host}"
+    port = f"port={port}"
+    user = f"user={user}"
+    deets = [dbname, host, port, user]
+    if pw is not None:
+        deets.append(f"password={pw}")
+    con_str = " ".join(deets)
+    return connect(con_str)
+
+
+def get_conn(context: str):
+    return create_conn(*get_deets(context))
+
+
+def build_engine(dbname: str,
+                 host: str,
+                 port: str,
+                 user: bool,
+                 pw: str = None
+                 ):
+    pre_sqlalc = "postgresql+psycopg2://"
+    post_sqlalc = f"@{host}:{port}/{dbname}"
+    if pw is None:
+        login = user
+    else:
+        login = f"{user}:{pw}"
+
+    con_str = pre_sqlalc + login + post_sqlalc
+    return create_engine(con_str)
+
+
+def get_engine(context: str):
+    return build_engine(*get_deets(context))
+
+
+def get_table_abrv(table_name: str):
+    parts = table_name.split("_")
[…]

### 2023-07-30 src/model/analysis.py

@@ -1,0 +1,798 @@
+# standard library imports
+from dataclasses import dataclass, field
+from datetime import datetime
+from itertools import chain
+from os import getenv
+
+# third party imports
+from tqdm import tqdm
+from baycomp import two_on_multiple
+import numpy as np
+from numpy import zeros, array, nan, isnan
+from matplotlib.colors import ListedColormap, BoundaryNorm
+from matplotlib.pyplot import subplots, title, legend
+from matplotlib.pyplot import tick_params, xlabel, ylabel
+from pandas import DataFrame, Series
+from seaborn import heatmap
+from scipy.stats import friedmanchisquare
+from scikit_posthocs import posthoc_nemenyi_friedman
+
+# eval and postprocessing
+from sklearn.metrics import roc_curve, roc_auc_score
+
+# local imports
+from db_helpers import DbHelper
+from utils import filter_df, keyslist, get_comb_gen
+from utils import set_envs, get_distinct_col_vals, istrue
+from utils import combine_domains, get_list_difs, get_idx_val, get_rect_area
+
+__range__ = range(-1, 3)
+# values
+LEFT, ROPE, RIGHT, OUT = __range__
+MID = ROPE
+
+# colors
+BLUE = (68/255, 155/255, 214/255, 1.)
+LIGHTGRAY = (.925, .925, .925, 1.)
+WHITE = LIGHTGRAY
+ORANGE = (222/255, 142/255, 8/255, 1.)
+GRAY = (.5, .5, .5, 1.)
+
+# decisions
+XGREATER = "X > Y"
+XLESS = "X < Y"
+NODECISION = "No Decision"
+XROPE = "ROPE"
+
+window_params = {
+    "bayes": {
+        "rgb": {
+            LEFT: BLUE,
+            ROPE: GRAY,
+            RIGHT: ORANGE,
+            OUT: WHITE,
+        },
+        "vals": {
+            LEFT: XGREATER,
+            ROPE: XROPE,
+            RIGHT: XLESS,
+            OUT: NODECISION,
+        },
+    },
+    "freq": {
+        "rgb": {
+            LEFT: BLUE,
+            MID: WHITE,
+            RIGHT: ORANGE,
+        },
+        "vals": {
+            LEFT: XGREATER,
+            MID: NODECISION,
+            RIGHT: XLESS,
+        },
+    },
+}
+
+if __name__ == "__main__":
+    set_envs("model")
+    dbh = DbHelper("LOCAL")
+
+
+class Abroca:
[…]

### 2023-07-30 src/model/preprocessing.py

@@ -1,0 +1,169 @@
+# standard library imports
+from os import getenv
+
+# third party imports
+from numpy import ravel, ascontiguousarray
+from pandas import DataFrame, Series
+
+# preprocessing
+from sklearn.compose import ColumnTransformer
+from sklearn.impute import SimpleImputer, KNNImputer
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import OneHotEncoder, StandardScaler
+
+# eval and postprocessing
+from sklearn.model_selection import train_test_split
+
+# local imports
+from db_helpers import Table
+from model.features import Features
+from utils import set_envs, set_nrows, set_rand_state, filter_df
+
+if __name__ == "__main__":
+    set_envs("model")
+
+
+class DataPrep:
+    cat_trans = Pipeline(
+        [
+            ("cat_imputer", SimpleImputer(strategy="constant", fill_value=0)),
+            ("onehot", OneHotEncoder(handle_unknown="ignore"))
+        ]
+    )
+    knn_num_trans = Pipeline(
+        [
+            ("knn_num_imputer", KNNImputer()),
+            ("scaler", StandardScaler())
+        ]
+    )
+    simp_num_trans = Pipeline(
+        [
+            ("num_imputer", SimpleImputer(strategy="constant", fill_value=0)),
+            ("scaler", StandardScaler())
+        ]
+    )
+    bool_trans = Pipeline(
+        [
+            ("bool_imputer", SimpleImputer(strategy="constant", fill_value=0))
+        ]
+    )
+
+    def get_data(self) -> DataFrame:
+        self.data = Table(getenv("CONTEXT"),
+                          self.schema,
+                          self.table,
+                          nrows=self.nrows)
+        return self.data.df
+
+    def set_y(self) -> Series:
+        y = self.df.loc[:, self.feat.to_predict_col]
+        self.y_1d = ravel(y)
+        return y
+
+    def set_X(self) -> DataFrame:
+        return self.df.loc[:, self.feat.keep_cols]
+
+    def sort_cols(self):
+        self.boolean_cols = self.feat.get_boolean_keep_cols()
+        self.categorical_cols = self.feat.get_categorical_keep_cols()
+        self.numeric_cols = self.feat.get_numeric_keep_cols()
+
+    def set_preprocessor(self):
+        if self.simple_num_impute:
+            num_trans = DataPrep.simp_num_trans
+        else:
+            num_trans = DataPrep.knn_num_trans
+
[…]

### 2023-07-30 src/utils.py

@@ -1,0 +1,261 @@
+from itertools import combinations as comb, chain
+from pathlib import Path
+from os import getenv
+
+from dotenv import load_dotenv
+from numpy import array
+from numpy.random import randint
+from matplotlib.pyplot import savefig
+
+from pandas import DataFrame, Series
+
+here = Path(__file__).parent.parent
+
+
+def set_envs(envname: str):
+    return load_dotenv(here / f".env.{envname}")
+
+
+def keyslist(_dict: dict):
+    return list(_dict.keys())
+
+
+def valslist(_dict: dict):
+    return list(_dict.values())
+
+
+def istrue(w: str):
+    return True if w == 'True' else False
+
+
+def isnone(x: str):
+    return True if (x == 'None' or x is None) else False
+
+
+def set_envint(y: str):
+    return None if isnone(y) else int(y)
+
+
+def set_nrows():
+    set_envint(getenv("NROWS"))
+
+
+def set_rand_state():
+    set_envint(getenv("RANDOM_STATE"))
+
+
+def get_distinct_col_vals(df: DataFrame, col: str):
+    return list(df.loc[:, col].unique())
+
+
+def filter_df(df: DataFrame, col: str, val: str):
+    return df[df.loc[:, col] == val]
+
+
+def series_col(df: DataFrame, col: str):
+    return Series(df.loc[:, col])
+
+
+def idx_list(nrows: int, ncols: int):
+    rrng = range(nrows)
+    crng = range(ncols)
+    return list(chain.from_iterable([[(i, j) for j in crng] for i in rrng]))
+
+
+def pathsearch(pattern: str, start_path: Path = here):
+    while True:
+        try:
+            return [x for x in start_path.rglob(pattern)][0]
+        except IndexError:
+            start_path = start_path.parent
+
+
+def figsave(figname: str,
+            figpath: Path = pathsearch("figures"),
+            format: str = "png",
+            **kwargs,  # use bb_inches=tight if cutoff
+            ):
+    fullpath = figpath / f"{figname}.{format}"
+    savefig(fullpath, format=format, **kwargs)
+    return fullpath.exists()
+
+
+def get_comb_gen(_list: list, _int: int):
+    for pair in comb(_list, _int):
+        yield pair
+
+
+def list_gen(_list: list,
+             rand: bool = False,
+             inf: bool = False
+             ):
+    _list = list(_list)
+    while True:
+        _len = len(_list)
+        if _len > 0:
[…]

### 2023-07-30 src/db_helpers.py
refactor with flake8

@@ -1,37 +1,319 @@
 # standard library imports
-from dataclasses import dataclass
-from math import log
+from math import log, sqrt
+from pathlib import Path
+from os import getenv
+from subprocess import Popen, PIPE
+from typing import Any
 
 # third party imports
 from matplotlib.pyplot import xticks, subplots
-from pandas import Series
+from numpy.random import choice
+from psycopg2 import connect
+from psycopg2.errors import UndefinedTable, ProgrammingError
+from pandas import read_sql, DataFrame, Series
 from seaborn import histplot
+from sqlalchemy import create_engine
 
-from alexlib.db.objects import Table, Column
-from alexlib.maths import get_props, euclidean_distance as pyth
-from setup import db_mgr as cnxn
+from utils import get_distinct_col_vals, get_props, series_col
+from utils import set_envs, filter_df, pathsearch
+
+set_envs("db")
+
+if getenv("CONTEXT") is None:
+    set_envs("model")
 
 
-class ProjectColumn(Column):
-    """A class to describe a column in a database table. Inherits from the Column class in the alexlib.db.objects module."""
+def onehot_case(col: str, val: str):
+    return f"case when {col} = '{val}' then 1 else 0 end"
 
-    @property
-    def is_id(self) -> bool:
-        """Returns True if the column name ends with '_id', else False."""
-        return False if self.col_name[-3:] != "_id" else True
 
-    def auto_xtick_angle(
-        self,
-        ndist_min: int = 5,
-        ndist_mult: int = 2,
-        len_min: int = 50,
-        len_mult: int = 2,
-        range_min: int = 100,
-        range_mult: int = 2,
-        text_min: int = 30,
-        text_mult: int = 2,
-    ) -> int:
-        """Returns the angle to rotate the x-axis labels in a histogram plot based on the number of unique values in the column, the length of the text in the unique values, the range of the frequency values, and the length of the series."""
+def pyth(_list: list):
+    return sqrt(sum([x ** 2 for x in _list]))
+
+
+def get_deets(context: str):
+    context = context.upper()
+    dbname = "DBNAME"
+    vars = ["DBHOST", "DBPORT", "DBSUDO"]
+    deets = [dbname] + [context + x for x in vars]
+    deets = [getenv(x) for x in deets]
+    return deets[0], deets[1], deets[2], deets[3]
+
+
+def create_conn(dbname: str,
+                host: str,
+                port: str,
+                user: bool,
[…]

### 2023-07-30 src/model/main.py

@@ -1,0 +1,95 @@
+# standard library imports
+from os import getenv
+from tqdm import tqdm
+
+# third party imports
+from numpy.random import choice
+
+# local imports
+from model.engine import ModelEngine
+from model.params import Params, model_types
+from model.features import Features
+from utils import set_envs, list_gen, istrue, pathsearch
+from db_helpers import DbHelper
+
+if __name__ == "__main__":
+    set_envs("model")
+    dbh = DbHelper("LOCAL")
+
+
+split_cols = ["is_stem", "is_female", "has_disability"]
+search_int = int(getenv("SEARCH_ITER"))
+grouped = istrue(getenv("SEARCH_GROUPED"))
+rand = istrue(getenv("SEARCH_RANDOM"))
+inf = istrue(getenv("INF_ITER"))
+schema = getenv("LOG_SCHEMA")
+reset_schema = istrue(getenv("RESET_SCHEMA"))
+
+feat_dict = {
+    "demographic": Features(to_include=split_cols, use_demographic=True),
+    "engagement": Features(to_include=split_cols, use_engagement=True),
+    "academic": Features(to_include=split_cols, use_academic=True),
+    "all": Features(to_include=split_cols, use_all=True),
+}
+feat_list = list(feat_dict.values())
+
+
+def rand_feat():
+    return [choice(feat_list)] if rand else feat_list
+
+
+def drop_tab_pattern(pattern: str,
+                     schema: str = schema,
+                     dbh: DbHelper = dbh,
+                     cascade: bool = True,
+                     ):
+    tabs = dbh.get_all_schema_tables(schema)
+    droptabs = [x for x in tabs if pattern in x]
+    for tab in droptabs:
+        dbh.drop_table(schema, tab, cascade=cascade)
+
+
+def run_all_models(schema: str = schema,
+                   reset_schema: bool = reset_schema,
+                   dbh: DbHelper = dbh
+                   ):
+    if reset_schema:
+        drop_tab_pattern("results")
+        drop_tab_pattern("param")
+        dbh.trunc_schema(schema)
+    model_gen = list_gen(model_types, rand=rand, inf=inf)
+    while True:
+        try:
+            model = next(model_gen)
+            for feat in tqdm(rand_feat()):
+                set_envs("model")
+                params = Params(model_type=model)
+                if grouped:
+                    m = ModelEngine(
+                        feat=feat,
+                        params=params
+                    )
+                    m.fit_test_log()
+                else:
+                    params_list = list(params.get_param_gen())
[…]

### 2023-07-30 src/file_helpers.py
refactor with flake8

@@ -1,0 +1,64 @@
+# standard library imports
+from pathlib import Path
+
+# third party imports
+from pandas import read_csv
+
+# local imports
+from db_helpers import build_engine, set_envs
+
+
+here = Path(__file__).parent
+set_envs(here)
+
+
+def get_info_schema(filename: str,
+                    dirpath: Path = here):
+    filepath = dirpath / filename
+    return read_csv(filepath, keep_default_na=False)
+
+
+def get_filepaths(dir: str, glob_pattern: str):
+    dirpath = here / dir
+    return [x for x in dirpath.rglob(glob_pattern)]
+
+
+def path_list_to_dict(path_list):
+    return {x.stem: x for x in path_list}
+
+
+def paths_to_df_dict(path_list):
+    return {x.stem: read_csv(x) for x in path_list}
+
+
+class FileHelper:
+    def insert_landing_tables(self):
+        engine = build_engine("learning")
+        total_rows = 0
+        for table in self.table_names:
+            df = self.source_df_dict[table]
+            df.to_sql(table,
+                      engine,
+                      if_exists="replace",
+                      schema="landing",
+                      index=False,
+                      chunksize=10000,
+                      method="multi"
+                      )
+            inserted_rows = len(df)
+            total_rows += inserted_rows
+            print(f"{inserted_rows} rows have been inserted into {table}")
+        print("total number of rows inserted:", total_rows)
+
+    def __init__(self):
+        self.source_csv_paths = get_filepaths("OULAD_dataset", "*.csv")
+        self.table_names = [x.stem for x in self.source_csv_paths]
+        self.source_df_dict = paths_to_df_dict(self.source_csv_paths)
+
+
+def copy_csv_str(table_name, csv_path):
+    return f"""COPY {table_name}
+    FROM '{csv_path}'
+    DELIMITER ','
+    CSV HEADER
+    """

### 2023-07-30 src/model/features.py

@@ -1,0 +1,173 @@
+# standard library imports
+from os import getenv
+from itertools import chain
+
+# third party imports
+from pandas import DataFrame
+
+# local imports
+from utils import filter_df, istrue, set_envs
+from db_helpers import Table
+
+if __name__ == '__main__':
+    set_envs("model")
+    print(getenv("PREDICT_COL"))
+
+
+class Features:
+    cat_cols = [
+        "course_id",
+        "module_id",
+        "presentation_id",
+    ]
+    to_drop_cols = [
+        "student_id",
+        "unreg_date",
+        "reg_date_dif"
+        ]
+    final_result_cols = [
+        'final_result',
+        'final_result_id',
+        'is_pass_or_distinction',
+        'is_distinction',
+        'is_pass',
+        'is_fail',
+        'is_withdrawn',
+        'is_withdraw_or_fail'
+        ]
+
+    def get_col_names(self,
+                      df: DataFrame
+                      ):
+        return df.loc[:, self.field_col]
+
+    def get_col_cat(self,
+                    ind_col: str,
+                    ind_val,
+                    ):
+        filtered_df = filter_df(self.tbl.df, ind_col, ind_val)
+        return list(self.get_col_names(filtered_df))
+
+    def set_col_cats(self):
+        self.all = self.get_col_names(self.tbl.df)
+        self.demographic = self.get_col_cat("is_demographics", 1)
+        self.academic = self.get_col_cat("is_academic", 1)
+        self.engagement = self.get_col_cat("is_engagement", 1)
+        self.final_result = self.get_col_cat("is_final_result", 1)
+        self.moment = self.get_col_cat("is_moment", 1)
+        self.student_info = self.get_col_cat("is_student_info", 1)
+        self.by_activity = self.get_col_cat("is_by_activity", 1)
+        self.obj = self.get_col_cat("is_obj", 1)
+        self.ids = self.get_col_cat("is_id", 1)
+        self.bool = self.get_col_cat("is_bool", 1)
+        self.num = [x for x in self.all if x not in self.obj + self.bool]
+
+    def get_keep_cols(self):
+        keep_cols = [self.to_include]
+        if self.use_academic:
+            keep_cols.append(self.academic)
+        if self.use_demographic:
+            keep_cols.append(self.demographic)
+        if self.use_engagement:
+            keep_cols.append(self.engagement)
+        if self.use_moments:
+            keep_cols.append(self.moment)
+        if self.use_student_info:
[…]

### 2023-07-30 src/model/logger.py

@@ -1,0 +1,109 @@
+# standard library imports
+from dataclasses import dataclass, field
+from datetime import datetime as dt
+from functools import partial
+from os import getenv
+
+# third party imports
+from pandas import DataFrame, concat
+from psycopg2.errors import DatatypeMismatch
+
+# local imports
+from utils import set_envs, keyslist
+from db_helpers import DbHelper
+
+if __name__ == "__main__":
+    set_envs("model")
+
+
+@dataclass
+class Logger:
+    model_type: str
+    log_schema: str = field(default=getenv("LOG_SCHEMA"))
+    log_runs_table: str = field(default="runs")
+    log_runs_id_col: str = field(default="id")
+    log_id_col: str = field(default="run_id")
+    log_data_table: str = field(default="data")
+    log_feat_table: str = field(default="feat")
+    log_results_table: str = field(default="results")
+    log_warnings_table: str = field(default="warnings")
+
+    def set_run_id(self):
+        return self.dbh.get_next_id(self.log_schema,
+                                    self.log_runs_table,
+                                    self.log_runs_id_col)
+
+    def get_table_attr(self):
+        return [x for x in list(self.__dict__.keys()) if "table" in x]
+
+    def add_run_id(self, _dict: dict):
+        _dict[self.log_id_col] = self.run_id
+        return _dict
+
+    def log_to_table(self, table: str, _dict: dict):
+        _dict = self.add_run_id(_dict)
+        self.send_log(table, _dict)
+
+    def set_partials(self):
+        self.log_warn = partial(self.log_to_table, self.log_warnings_table)
+        self.log_params = partial(self.log_to_table, self.log_params_table)
+        self.log_feat = partial(self.log_to_table, self.log_feat_table)
+        self.log_data = partial(self.log_to_table, self.log_data_table)
+        self.log_results = partial(self.log_to_table, self.log_results_table)
+
+    def __post_init__(self):
+        self.dbh = DbHelper(getenv("CONTEXT"))
+        self.cv_results = getenv("CV_RESULTS")
+        ptab = f"params_{self.model_type}"
+        if self.cv_results == "ALL":
+            self.log_results_table = self.log_results_table + "_all"
+        self.log_params_table = ptab
+        self.if_exists = "append"
+        self.run_id = self.set_run_id()
+        self.tables = self.get_table_attr()
+        self.set_partials()
+
+    def send_log(self,
+                 log_table: str,
+                 _dict: dict,
+                 ):
+        cvisall = self.cv_results == "ALL"
[…]

### 2023-07-30 dev/norm_mvsk.py
refactor with flake8

@@ -1,0 +1,26 @@
+mvsk = [0,1,1,3]
+m1, v1, s1, k1 = 0.05, 1.04, 1.01, 1.41
+iters = 30
+xn = iters ** 2
+xmin, xmax = mvsk[0] - (mvsk[1] * (v1 ** iters)), mvsk[0] + (mvsk[1] * (v1 ** iters))
+
+fig = plt.figure()
+axis = plt.axes()
+line, = axis.plot([], [])
+def init():
+    line.set_data([], [])
+    return line,
+
+x = linspace(xmin, xmax, xn)
+
+color = iter(cm.plasma(linspace(1,0,iters)))
+
+
+for i in range(iters):
+    mvsk[0] = mvsk[0] + (m1)
+    mvsk[1] = mvsk[1] * (v1)
+    mvsk[2] = mvsk[2] * (s1 ** i) + abs(s1)
+    mvsk[3] = mvsk[3] * (k1)
+    c = next(color)
+    pdf = extras.pdf_mvsk(mvsk)
+    plt.plot(x, pdf(x), c=c)

### 2023-07-30 src/model/engine.py

@@ -1,0 +1,315 @@
+# standard library imports
+from os import getenv
+from warnings import catch_warnings
+
+# third party imports
+from numpy import array
+from pandas import DataFrame, Series
+
+# preprocessing
+from sklearn.decomposition import PCA
+from sklearn.feature_selection import VarianceThreshold
+from sklearn.pipeline import Pipeline
+
+# eval and postprocessing
+from sklearn.metrics import classification_report, confusion_matrix
+from sklearn.model_selection import RepeatedStratifiedKFold
+
+# local imports
+from pkg.src.model.analysis import RocCurve
+from pkg.src.model.logger import Logger
+from pkg.src.model.params import Params
+from pkg.src.model.preprocessing import DataPrep
+from pkg.src.model.features import Features
+from utils import istrue, overwrite_std_params, keyslist
+
+from utils import set_envs
+set_envs("model")
+LEFT, ROPE, RIGHT, OUT = range(-1, 3)
+
+
+class ModelEngine:
+    def get_crossval(
+        self,
+        n_splits=None,
+        n_repeats=None
+    ):
+        if n_splits is None:
+            n_splits = int(getenv("CV_NSPLITS"))
+        if n_repeats is None:
+            n_repeats = int(getenv("CV_NREPEATS"))
+        rskf = RepeatedStratifiedKFold(
+            n_splits=n_splits,
+            n_repeats=n_repeats,
+            random_state=self.params.random_state
+        )
+        self.n_splits = n_splits
+        self.n_repeats = n_repeats
+        return rskf
+
+    def set_data(self):
+        data = DataPrep(
+            self.feat,
+            nrows=self.params.nrows,
+            test_size=self.params.test_size,
+            random_state=self.params.random_state,
+            simple_num_impute=istrue(getenv("SIMPLE_NUM_IMPUTE")),
+            df_filter=self.df_filter
+        )
+        return data
+
+    def get_pipe(self):
+        prep = ("preprocessing", self.data.preprocessor)
+        var_thresh = ("var_thresh", VarianceThreshold())
+        dim_reduce = ("dim_reduce", PCA(n_components="mle"))
+        clf = ("clf", self.params.clf())
+        steps = [prep, var_thresh, clf]
+        if self.reduce_dim:
+            steps.insert(2, dim_reduce)
+        return Pipeline(steps)
+
+    def set_gridsearch(
+        self,
+        scoring: list = [
+            # "f1",
+            # "precision",
[…]

### 2023-07-30 src/model/params.py

@@ -1,0 +1,430 @@
+# standard library imports
+from dataclasses import dataclass, field
+from os import getenv
+
+# third party imports
+from scipy.stats import expon, uniform
+
+# local imports
+from utils import set_envs, set_nrows, set_rand_state, istrue
+
+if __name__ == "__main__":
+    set_envs("model")
+
+
+jobint = int(getenv("JOB_CORES"))
+model_types = [
+    "hxg_boost",
+    "logreg",
+    "rforest",
+    "ada_boost",
+    "etree",
+    "dtree",
+    "knn",
+    "mlp",
+    "svc",
+    # "compnb",
+    # "gauss",
+]
+
+
+def discrete_exp_dist(
+        exp_min: int,
+        exp_max: int,
+        exp_int: int = 10,
+        exp_inc: int = 1,
+        numerator: int = 1
+):
+    exp_max += 1
+    rng = range(exp_min, exp_max, exp_inc)
+    return [numerator / (exp_int ** i) for i in rng]
+
+
+def wrap_dict_vals(_dict):
+    for key in list(_dict.keys()):
+        val = _dict[key]
+        _dict[key] = [val]
+    return _dict
+
+
+@dataclass
+class Params:
+    model_type: int = getenv("MODEL_TYPE")
+    predict_col: int = getenv("PREDICT_COL")
+    nrows: int = set_nrows()
+    test_size: float = float(getenv("TEST_SIZE"))
+    random_state: int = set_rand_state()
+    params: dict = field(default_factory=dict)
+
+    def set_rand_param_dict(self):
+
+        # slight better performance noticed without warm start
+        _bool = [True, False]
+        if self.model_type == "logreg":
+            params = [
+                {
+                    "clf__solver": [
+                        "lbfgs",
+                        "sag",
+                        "newton-cg",
+                        "newton-cholesky"
+                        ],
+                    "clf__penalty": [None, "l2"],
+                    "clf__C": expon(scale=0.1),
+                    # "clf__warm_start": [False],
+                    "clf__max_iter": [i for i in range(30, 150)],
+                    "clf__random_state": [self.random_state],
+                    "clf__n_jobs": [jobint],
+                },
+                {
+                    "clf__solver": ["saga"],
+                    "clf__penalty": [None, "l2", "l1"],
+                    "clf__C": expon(scale=0.1),
+                    # "clf__l1_ratio": uniform(),
+                    "clf__warm_start": _bool,
+                    # "clf__max_iter": max_iter_dist,
[…]

### 2024-02-03 dev/norm_mvsk.py
add git lfs rm push - push to other branch

@@ -1,26 +1,0 @@
-mvsk = [0,1,1,3]
-m1, v1, s1, k1 = 0.05, 1.04, 1.01, 1.41
-iters = 30
-xn = iters ** 2
-xmin, xmax = mvsk[0] - (mvsk[1] * (v1 ** iters)), mvsk[0] + (mvsk[1] * (v1 ** iters))
-
-fig = plt.figure()
-axis = plt.axes()
-line, = axis.plot([], [])
-def init():
-    line.set_data([], [])
-    return line,
-
-x = linspace(xmin, xmax, xn)
-
-color = iter(cm.plasma(linspace(1,0,iters)))
-
-
-for i in range(iters):
-    mvsk[0] = mvsk[0] + (m1)
-    mvsk[1] = mvsk[1] * (v1)
-    mvsk[2] = mvsk[2] * (s1 ** i) + abs(s1)
-    mvsk[3] = mvsk[3] * (k1)
-    c = next(color)
-    pdf = extras.pdf_mvsk(mvsk)
-    plt.plot(x, pdf(x), c=c)

### 2024-02-03 __init__.py
rm load_dotenv reference rm temp files

@@ -1,7 +1,5 @@
 from pathlib import Path
 from sys import path
+
 path.append(str(Path(__file__).parent.parent))
 path.append(str(Path(__file__).parent / "src"))
-
-from dotenv import load_dotenv
-load_dotenv()

### 2024-02-04 paper/paper.tex
Update LaTeX build configuration

@@
 \usepackage{graphicx}
-\graphicspath{ {../figures/} }
+\usepackage{hyperref}
+\graphicspath{ {../figures} }
 
@@
 
-        Selecting the approriate model to deploy should involve the consideration of many factors.
+        Selecting the appropriate model to deploy should involve the consideration of many factors.
         Predictive performance is important, but simply picking the model with the highest mean accuracy is not a valid strategy.
@@
         \subsubsection{Featuresets}
-            The most common featuresets for predicting student outcomes are are academic, demographic, and behavioral \cite{engage2014,eval2018,early2019,assign2021esteban,compare2015}.
+            The most common featuresets for predicting student outcomes are academic, demographic, and behavioral \cite{engage2014,eval2018,early2019,assign2021esteban,compare2015}.
             Academic includes information about assessments and assignments \cite{assign2021esteban}.
@@
         \subsubsection{Naive Averaging}
-            Naive averaging is the evaluation tactic by which models are evaluated by ranking by the average of the target metric between runs an that alone. 
-            This strategy is both common and problemtatic because it doesn't take into account the magnitude and variability of differences in performance \cite{eval2018}.
+            Naive averaging is the evaluation tactic by which models are evaluated by ranking by the average of the target metric between runs and that alone. 
+            This strategy is both common and problematic because it doesn't take into account the magnitude and variability of differences in performance \cite{eval2018}.
 
@@
                 A model that produces equivalent prediction probabilities for the subgroups of the split dataset equally would have ABROCA = 0. 
-                Producing the same prediction probabilities wouldproduce the same ROC curves, so there would be no area to sum.
+                Producing the same prediction probabilities would produce the same ROC curves, so there would be no area to sum.
                 Hypothesis - Higher ABROCA associated with lower predictive fairness
@@
             The three remaining tables bridge the student demographic table with each of the course tables. 
-            One table contains the inforamiton about course registration.
+            One table contains the information about course registration.
             One summarizes students' interactions with individual VLE activities on a daily timescale.
@@
             \subsubsection{Flat Files to Main}
-                The first step in utilizing the database was injesting the data.
+                The first step in utilizing the database was ingesting the data.
                 I used the Python package pandas to load the Comma-Separated Values (CSV) files into a schema called [landing].
@@
                     \centering
-                    \includegraphics[width=1\textwidth]{n_days_active}
+                    \includegraphics[width=1\linewidth]{n_days_active}
                     \caption{The number of distinct days that students interacted with the VLE in the first 30 days}
@@
                     \centering
-                    \includegraphics[width=1\textwidth]{n_total_clicks_by_top_5th_clicks}
+                    \includegraphics[width=1\linewidth]{n_total_clicks_by_top_5th_clicks}
                     \caption{The total number of clicks on activities ranked in the top 5th percentile of activities as measured by student clicks}
@@
             Hyperparameters are the input parameters for the operation of a machine learning model.
-            All of the algortihms and parameter selection components I used are part the Python package scikit-learn \cite{sklearn}
+            All of the algorithms and parameter selection components I used are part the Python package scikit-learn \cite{sklearn}
             \subsubsection{Hyperparameter Selection}
-                I utlized two different strategies for parameter selection: GridSearch and RandomSearch.
+                I utilized two different strategies for parameter selection: GridSearch and RandomSearch.
                 GridSearch is a brute force strategy where one can specify collections of parameter selections and the cross-validating object will walk through them all. 
@@
                 If models were taking longer than 30 minutes to run, I moved the limits of the parameter selection ranges to avoid that when possible.
-                The optimization algorithms used to train these models can sometimes not converge to a local (ideally global) minimum, meaning that the predictions will not be the ebst, which is why restricting the paramter ranges is necessary.
+                The optimization algorithms used to train these models can sometimes not converge to a local (ideally global) minimum, meaning that the predictions will not be the best, which is why restricting the parameter ranges is necessary.
 
-                Once the paramter ranges were sufficiently restricted, I ran my model-generating pipeline using the RandomSearch strategy.
-                This can be advantegous because certain combinations of parameter values will never be tried on a reasonable timescale while using a brute force strategy.
+                Once the parameter ranges were sufficiently restricted, I ran my model-generating pipeline using the RandomSearch strategy.
+                This can be advantageous because certain combinations of parameter values will never be tried on a reasonable timescale while using a brute force strategy.
 
@@
             \subsubsection{Data Preprocessing}
-                In the data preprocessing pipeline, features were transformed in order to improve their compatability with making predictions.
+                In the data preprocessing pipeline, features were transformed in order to improve their compatibility with making predictions.
                 Categorical data was encoded using the "one hot" strategy where each value was pivoted into a Boolean feature.    
@@
                 Another strategy implemented to increase efficiency is Principle Component Analysis (PCA) using a Maximum-Likelihood Estimator (MLE) strategy.
-                Similar to the variance threshold, PCA works by reducing model dimensionality in orer to reduce model training time, though through a more complex process.
+                Similar to the variance threshold, PCA works by reducing model dimensionality in order to reduce model training time, though through a more complex process.
 
@@
         I wanted to make as few assumptions as possible about the distribution of the underlying data.
-        Additionally, since cross-validation was used, we shouldn't use a ttest \cite{why2009, eval2018}.
+        Additionally, since cross-validation was used, we shouldn't use a t-test \cite{why2009, eval2018}.
 
@@
         Even looking at the top two approximately-equivalent regions, the top six of seven are tree-based ensemble methods, similar to research.
-        Surprisingly there ain't an Ada Boostingup there.
+        Surprisingly there ain't an Ada Boosting model up there.
 
@@
 
-        The top four models happened to be different model types, so I retrained and evaluated the ABROCA for each model on each distict course's data.
+        The top four models happened to be different model types, so I retrained and evaluated the ABROCA for each model on using the data mined from each distinct course.
         The points on each chart represent an individual model's ABROCA score for an individual course, differentiate by color for each course domain. 
@@
     \subsection{Best Evaluation Method}
-        Similar to expectations, we found that Bayesian evaluation methods produced the most conclusive answer to the "which model is better question" and suffers from the fewest assumptions or invalidations.
+        Similar to expectations, I found that Bayesian evaluation methods produced the most conclusive answer to the "which model is better question" and suffers from the fewest assumptions or invalidations.
 
     \subsection{Fairness vs Performance}
-        We did not see a strong relationship between model predictive performance (as measured by ROC AUC) and ABROCA.
-        There did appear to be a strong relationhip between demographic ratio and ABROCA.
+        I did not see a strong relationship between model predictive performance (as measured by ROC AUC) and ABROCA.
+        There did appear to be a strong relationship between demographic ratio and ABROCA.
         This result seems to indicate the ABROCA may be a useful metric in the evaluation of model fairness.
@@
         An attempt could be made to integrate it into the model selection process.
-        One might explore if a higher-dimension expression of the calculation holds water (get it, volume).
-        More of the mathetmatical properties of ABROCA could be explored.
+        One might explore if a higher-dimension expression of the calculation holds water.
+        More of the mathematical properties of ABROCA could be explored.
 

### 2024-02-04 src/db_helpers.py
Add pytest coverage options to pyproject.toml add additional docstrings

@@ -7,9 +7,9 @@ from matplotlib.pyplot import xticks, subplots
 from pandas import Series
 from seaborn import histplot
 
-from alexlib.db import Table, Column
+from alexlib.db.objects import Table, Column
 from alexlib.maths import get_props, euclidean_distance as pyth
-from setup import cnxn
+from setup import db_mgr as cnxn
 
 
 class ProjectColumn(Column):
@@ -17,16 +17,17 @@ class ProjectColumn(Column):
     def is_id(self):
         return False if self.col_name[-3:] != "_id" else True
 
-    def auto_xtick_angle(self,
-                         ndist_min: int = 5,
-                         ndist_mult: int = 2,
-                         len_min: int = 50,
-                         len_mult: int = 2,
-                         range_min: int = 100,
-                         range_mult: int = 2,
-                         text_min: int = 30,
-                         text_mult: int = 2
-                         ):
+    def auto_xtick_angle(
+        self,
+        ndist_min: int = 5,
+        ndist_mult: int = 2,
+        len_min: int = 50,
+        len_mult: int = 2,
+        range_min: int = 100,
+        range_mult: int = 2,
+        text_min: int = 30,
+        text_mult: int = 2,
+    ):
         uni = list(self.series.unique())
         self.ndist = len(uni)
         if self.ndist < ndist_min:
@@ -54,42 +55,39 @@ class ProjectColumn(Column):
             _range = 0
         self.logrange_prod = range_mult * _range
 
-        to_pyth = [
-            self.len_prod,
-            self.ndist_prod,
-            self.logrange_prod,
-            self.text_prod
-        ]
+        to_pyth = [self.len_prod, self.ndist_prod, self.logrange_prod, self.text_prod]
         angle = int(pyth(to_pyth))
         if angle > 45:
             return 45
         else:
             return angle
 
-    def __init__(self,
-                 schema: str,
-                 table: str,
-                 col_name: str,
-                 series: Series,
-                 ) -> None:
+    def __init__(
+        self,
+        schema: str,
+        table: str,
+        col_name: str,
+        series: Series,
+    ) -> None:
         self.schema = schema
         self.table = table
         self.col_name = col_name
         self.series = series
 
-    def desc(self,
-             show_props: bool = False,
-             show_nulls: bool = False,
-             show_series_desc: bool = False,
-             show_hist: bool = False,
-             **kwargs
-             ):
+    def desc(
+        self,
+        show_props: bool = False,
+        show_nulls: bool = False,
[…]

### 2024-02-04 __init__.py
Add pytest coverage options to pyproject.toml add additional docstrings

@@ -1,7 +1,0 @@
-from pathlib import Path
-from sys import path
-path.append(str(Path(__file__).parent.parent))
-path.append(str(Path(__file__).parent / "src"))
-
-from dotenv import load_dotenv
-load_dotenv()

### 2024-02-04 src/analysis.py

@@ -14,82 +14,37 @@ from scipy.stats import friedmanchisquare
 from scikit_posthocs import posthoc_nemenyi_friedman
 from sklearn.metrics import roc_curve, roc_auc_score
 
-# local imports
-from alexlib.db import Connection
+from alexlib.db.managers import PostgresManager
 from alexlib.df import filter_df, get_distinct_col_vals
 from alexlib.core import chkenv
 from alexlib.iters import get_comb_gen, get_idx_val, link
 from alexlib.maths import combine_domains, get_list_difs, get_rect_area
-from setup import config
+from setup import config, db_mgr
+from constants import WINDOWPANE_PLOT_PARAMS, MID, LEFT, RIGHT, OUT, ROPE
 
-__range__ = range(-1, 3)
-# values
-LEFT, ROPE, RIGHT, OUT = __range__
-MID = ROPE
-
-# colors
-BLUE = (68 / 255, 155 / 255, 214 / 255, 1.)
-LIGHTGRAY = (.925, .925, .925, 1.)
-WHITE = LIGHTGRAY
-ORANGE = (222 / 255, 142 / 255, 8 / 255, 1.)
-GRAY = (.5, .5, .5, 1.)
-
-# decisions
-XGREATER = "X > Y"
-XLESS = "X < Y"
-NODECISION = "No Decision"
-XROPE = "ROPE"
-
-window_params = {
-    "bayes": {
-        "rgb": {
-            LEFT: BLUE,
-            ROPE: GRAY,
-            RIGHT: ORANGE,
-            OUT: WHITE,
-        },
-        "vals": {
-            LEFT: XGREATER,
-            ROPE: XROPE,
-            RIGHT: XLESS,
-            OUT: NODECISION,
-        },
-    },
-    "freq": {
-        "rgb": {
-            LEFT: BLUE,
-            MID: WHITE,
-            RIGHT: ORANGE,
-        },
-        "vals": {
-            LEFT: XGREATER,
-            MID: NODECISION,
-            RIGHT: XLESS,
-        },
-    },
-}
 
 if __name__ == "__main__":
     config
-    dbh = Connection.from_context("LOCAL")
+    dbh = db_mgr.cnxn_mgr
 
 
 class Abroca:
-    def extend_tpr(self,
-                   old_x: list,
-                   old_y: list,
-                   ):
+    def extend_tpr(
+        self,
+        old_x: list,
+        old_y: list,
+    ):
         new_y = []
         idx_counter = 0
         for i in range(self.dlen):
[…]

### 2024-02-04 src/constants.py

@@ -1,0 +1,68 @@
+"""Constants for the project."""
+from pathlib import Path
+
+
+HOME = Path.home()
+PROJECT_PATH = HOME / "repos/master_proj"
+DATA_PATH = PROJECT_PATH / "data"
+QUERY_PATH = PROJECT_PATH / "queries"
+MODEL_TYPES = [
+    "hxg_boost",
+    "logreg",
+    "rforest",
+    "ada_boost",
+    "etree",
+    "dtree",
+    "knn",
+    "mlp",
+    "svc",
+    # "compnb",
+    # "gauss",
+]
+
+__range__ = range(-1, 3)
+# rope values
+LEFT, ROPE, RIGHT, OUT = __range__
+MID = ROPE
+
+# windowpane plot colors
+BLUE = (68 / 255, 155 / 255, 214 / 255, 1.0)
+LIGHTGRAY = (0.925, 0.925, 0.925, 1.0)
+WHITE = LIGHTGRAY
+ORANGE = (222 / 255, 142 / 255, 8 / 255, 1.0)
+GRAY = (0.5, 0.5, 0.5, 1.0)
+
+# model comparison decisions
+XGREATER = "X > Y"
+XLESS = "X < Y"
+NODECISION = "No Decision"
+XROPE = "ROPE"
+
+WINDOWPANE_PLOT_PARAMS = {
+    "bayes": {
+        "rgb": {
+            LEFT: BLUE,
+            ROPE: GRAY,
+            RIGHT: ORANGE,
+            OUT: WHITE,
+        },
+        "vals": {
+            LEFT: XGREATER,
+            ROPE: XROPE,
+            RIGHT: XLESS,
+            OUT: NODECISION,
+        },
+    },
+    "freq": {
+        "rgb": {
+            LEFT: BLUE,
+            MID: WHITE,
+            RIGHT: ORANGE,
+        },
+        "vals": {
+            LEFT: XGREATER,
+            MID: NODECISION,
+            RIGHT: XLESS,
+        },
+    },
+}

### 2024-02-04 src/logger.py

@@ -1,19 +1,16 @@
-# standard library imports
 from dataclasses import dataclass, field
 from datetime import datetime as dt
 from functools import partial
 
-# third party imports
 from pandas import DataFrame, concat
-from psycopg2.errors import DatatypeMismatch
+from psycopg.errors import DatatypeMismatch
 
-# local imports
-from alexlib.config import chkenv
-from alexlib.iters import keys
-from setup import dbh
+from alexlib.core import chkenv
+from setup import db_mgr as cnxn
 
 if __name__ == "__main__":
     from setup import config
+
     config
 
 
@@ -30,12 +27,12 @@ class Logger:
     log_warnings_table: str = field(default="warnings")
 
     def set_run_id(self):
-        return self.dbh.get_next_id(self.log_schema,
-                                    self.log_runs_table,
-                                    self.log_runs_id_col)
+        return cnxn.get_next_id(
+            self.log_schema, self.log_runs_table, self.log_runs_id_col
+        )
 
     def get_table_attr(self):
-        return [x for x in list(self.__dict__.keys()) if "table" in x]
+        return [x for x in self.__dict__.keys() if "table" in x]
 
     def add_run_id(self, _dict: dict):
         _dict[self.log_id_col] = self.run_id
@@ -53,7 +50,6 @@ class Logger:
         self.log_results = partial(self.log_to_table, self.log_results_table)
 
     def __post_init__(self):
-        self.dbh = dbh
         self.cv_results = chkenv("CV_RESULTS")
         ptab = f"params_{self.model_type}"
         if self.cv_results == "ALL":
@@ -64,26 +60,24 @@ class Logger:
         self.tables = self.get_table_attr()
         self.set_partials()
 
-    def send_log(self,
-                 log_table: str,
-                 _dict: dict,
-                 ):
+    def send_log(
+        self,
+        log_table: str,
+        _dict: dict,
+    ):
         cvisall = self.cv_results == "ALL"
-        if (cvisall and ("param" in log_table or "result" in log_table)):
+        if cvisall and ("param" in log_table or "result" in log_table):
             list_dict = _dict
         else:
-            list_dict = {x: [_dict[x]] for x in keys(_dict)}
+            list_dict = {v: [v] for k, v in _dict.items()}
 
         df = DataFrame.from_dict(list_dict)
-        if ("param" in log_table or "result" in log_table):
-            df.reset_index(
-                inplace=True,
-                names="iter_id"
-            )
[…]

### 2024-02-04 src/main.py

@@ -3,13 +3,14 @@ from random import choice
 from tqdm import tqdm
 
 # local imports
-from alexlib.db import Connection
+from alexlib.db.managers import PostgresManager
 from alexlib.core import chkenv
 from alexlib.iters import list_gen
 from engine import ModelEngine
-from params import Params, model_types
+from params import Params
 from features import Features
-from setup import cnxn, random_state
+from constants import MODEL_TYPES
+from setup import db_mgr as cnxn, random_state
 
 
 split_cols = ["is_stem", "is_female", "has_disability"]
@@ -35,31 +36,25 @@ def rand_feat():
 def run_all_models(
     schema: str = schema,
     reset_schema: bool = reset_schema,
-    cnxn: Connection = cnxn
+    cnxn: PostgresManager = cnxn,
 ) -> bool:
     if reset_schema:
         cnxn.drop_table_pattern("results")
         cnxn.drop_table_pattern("param")
         cnxn.truncate_schema(schema)
-    model_gen = list_gen(model_types, rand=random_state, inf=inf)
+    model_gen = list_gen(MODEL_TYPES, rand=random_state, inf=inf)
     while True:
         try:
             model = next(model_gen)
             for feat in tqdm(rand_feat()):
                 params = Params(model_type=model)
                 if grouped:
-                    m = ModelEngine(
-                        feat=feat,
-                        params=params
-                    )
+                    m = ModelEngine(feat=feat, params=params)
                     m.fit_test_log()
                 else:
                     params_list = list(params.get_param_gen())
                     for param in params_list:
-                        m = ModelEngine(
-                            feat=feat,
-                            params=param
-                        )
+                        m = ModelEngine(feat=feat, params=param)
                         m.fit_test_log()
         except StopIteration:
             return True

### 2024-02-04 src/setup.py

@@ -1,37 +1,21 @@
+"""Setup for the project."""
 from logging import WARNING
-from pathlib import Path
 
 from alexlib.auth import Auth
-from alexlib.config import DotEnv
+from alexlib.files.config import DotEnv
 from alexlib.core import chkenv
-from alexlib.db import Connection
+from alexlib.db.managers import PostgresManager
+
+from constants import PROJECT_PATH
 
 config = DotEnv.from_path(
-    Path(__file__).parent.parent / ".env",
+    PROJECT_PATH / ".env",
     loglevel=WARNING,
     eventlevel=WARNING,
 )
-home = Path.home()
-proj = home / "repos/master_proj"
-data = proj / "data"
-queries = proj / "queries"
 auth = Auth("local.sudo.learning")
-cnxn = Connection.from_auth(auth)
+db_mgr = PostgresManager.from_auth(auth)
 
 nrows = chkenv("NROWS", astype=int, need=False)
 random_state = chkenv("RANDOM_STATE", astype=int, need=False)
 jobint = chkenv("JOB_CORES", astype=int)
-
-model_types = [
-    "hxg_boost",
-    "logreg",
-    "rforest",
-    "ada_boost",
-    "etree",
-    "dtree",
-    "knn",
-    "mlp",
-    "svc",
-    # "compnb",
-    # "gauss",
-]

### 2024-02-04 paper/paper.tex
Update build and clean scripts, and fix hyperlink color in paper.tex

@@
 \usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=black,
+    filecolor=black,
+    citecolor=black,    
+    urlcolor=black,
+}
 \graphicspath{ {../figures} }
@@
             \subsubsection{Database System}
-                I chose to create a PostgreSQL relational database to organize the cleansing pipeline for this project \cite{postrgesql}.
+                I chose to create a PostgreSQL relational database to organize the cleansing pipeline for this project \cite{postgresql}.
                 PostgreSQL is an open source, performant, and reliable relational database system. 

### 2024-02-04 src/analysis.py
add docstrings

@@ -1,3 +1,4 @@
+"""A module for analyzing the results of a model run."""
 from dataclasses import dataclass, field
 from datetime import datetime
 
@@ -29,11 +30,14 @@ if __name__ == "__main__":
 
 
 class Abroca:
+    """A class for calculating the area between two ROC curves."""
+
     def extend_tpr(
         self,
         old_x: list,
         old_y: list,
-    ):
+    ) -> list:
+        """Extend the TPR to the new domain."""
         new_y = []
         idx_counter = 0
         for i in range(self.dlen):
@@ -52,40 +56,48 @@ class Abroca:
                 new_y.append(new_y[-1])
         return array(new_y)
 
-    def get_new_tpr(self, roc):
+    def get_new_tpr(self, roc) -> list:
+        """Get the new TPR for the new domain."""
         x = list(roc.fpr)
         y = list(roc.tpr)
         return self.extend_tpr(x, y)
 
-    def set_new_tprs(self):
+    def set_new_tprs(self) -> None:
+        """Set the new TPRs for the new domain."""
         self.new_tpr1 = self.get_new_tpr(self.roc1)
         self.new_tpr2 = self.get_new_tpr(self.roc2)
 
-    def set_domain(self):
+    def set_domain(self) -> None:
+        """Set the domain for the new TPRs."""
         self.domain = combine_domains(self.roc1.fpr, self.roc2.fpr)
         self.ddifs = get_list_difs(self.domain)
         self.dlen = len(self.domain)
 
-    def get_abroca(self):
+    def get_abroca(self) -> float:
+        """Get the ABROCA."""
         y1 = self.new_tpr1
         y2 = self.new_tpr2
         yrange = range(len(y1))
         heights = [y1[i] - y2[i] for i in yrange][1:]
         return get_rect_area(heights, self.ddifs)
 
-    def set_abroca(self):
+    def set_abroca(self) -> None:
+        """Set the ABROCA."""
         self.abroca = self.get_abroca()
 
-    def steps(self):
+    def steps(self) -> None:
+        """Run the steps for the class."""
         self.set_domain()
         self.set_new_tprs()
         self.set_abroca()
 
     @property
     def keys(self) -> list[str]:
+        """Get the keys for the curves."""
         return list(self.curves.keys())
 
     def __init__(self, split_col: str, curve_dict: dict) -> None:
+        """Initialize the class."""
         self.split_col = split_col
         self.roc1 = curve_dict[self.keys[0]]
[…]

### 2024-02-04 src/db_helpers.py

@@ -13,8 +13,11 @@ from setup import db_mgr as cnxn
 
 
 class ProjectColumn(Column):
+    """A class to describe a column in a database table. Inherits from the Column class in the alexlib.db.objects module."""
+
     @property
-    def is_id(self):
+    def is_id(self) -> bool:
+        """Returns True if the column name ends with '_id', else False."""
         return False if self.col_name[-3:] != "_id" else True
 
     def auto_xtick_angle(
@@ -27,7 +30,8 @@ class ProjectColumn(Column):
         range_mult: int = 2,
         text_min: int = 30,
         text_mult: int = 2,
-    ):
+    ) -> int:
+        """Returns the angle to rotate the x-axis labels in a histogram plot based on the number of unique values in the column, the length of the text in the unique values, the range of the frequency values, and the length of the series."""
         uni = list(self.series.unique())
         self.ndist = len(uni)
         if self.ndist < ndist_min:
@@ -69,6 +73,7 @@ class ProjectColumn(Column):
         col_name: str,
         series: Series,
     ) -> None:
+        """Initializes the ProjectColumn object. Inherits from the Column class in the alexlib.db.objects module."""
         self.schema = schema
         self.table = table
         self.col_name = col_name
@@ -81,7 +86,8 @@ class ProjectColumn(Column):
         show_series_desc: bool = False,
         show_hist: bool = False,
         **kwargs,
-    ):
+    ) -> tuple:
+        """Describes the column in the database table. Returns a tuple containing the figure and axis of the histogram plot."""
         try:
             to_pyth = [
                 self.len_prod,
@@ -131,19 +137,24 @@ class ProjectColumn(Column):
 
 @dataclass
 class ProjectTable(Table):
-    def __post_init__(self):
+    """A class to describe a database table. Inherits from the Table class in the alexlib.db.objects module."""
+
+    def __post_init__(self) -> None:
+        """Initializes the ProjectTable object. Inherits from the Table class in the alexlib.db.objects module."""
         if self.df is None:
             self.df = cnxn.get_table(
                 self.schema,
-                self.table,
+                self.name,
                 nrows=self.nrows,
             )
 
-    def desc_col(self, col: str, **kwargs):
+    def desc_col(self, col: str, **kwargs) -> None:
+        """Describes a column in the database table. Returns a tuple containing the figure and axis of the histogram plot."""
         col = self.cols[col]
         col.desc(**kwargs)
 
[…]

### 2024-02-04 src/logger.py

@@ -16,6 +16,8 @@ if __name__ == "__main__":
 
 @dataclass
 class Logger:
+    """A class to log the results of a model to a database table. Inherits from the ProjectTable class"""
+
     model_type: str
     log_schema: str = field(default=chkenv("LOG_SCHEMA"))
     log_runs_table: str = field(default="runs")
@@ -26,30 +28,36 @@ class Logger:
     log_results_table: str = field(default="results")
     log_warnings_table: str = field(default="warnings")
 
-    def set_run_id(self):
+    def set_run_id(self) -> int:
+        """Returns the next id for the runs table."""
         return cnxn.get_next_id(
             self.log_schema, self.log_runs_table, self.log_runs_id_col
         )
 
-    def get_table_attr(self):
+    def get_table_attr(self) -> list:
+        """Returns a list of the table attributes of the Logger object."""
         return [x for x in self.__dict__.keys() if "table" in x]
 
-    def add_run_id(self, _dict: dict):
+    def add_run_id(self, _dict: dict) -> dict:
+        """Adds the run_id to a dictionary."""
         _dict[self.log_id_col] = self.run_id
         return _dict
 
-    def log_to_table(self, table: str, _dict: dict):
+    def log_to_table(self, table: str, _dict: dict) -> None:
+        """Logs a dictionary to a database table."""
         _dict = self.add_run_id(_dict)
         self.send_log(table, _dict)
 
-    def set_partials(self):
+    def set_partials(self) -> None:
+        """Sets the partial functions for the Logger object."""
         self.log_warn = partial(self.log_to_table, self.log_warnings_table)
         self.log_params = partial(self.log_to_table, self.log_params_table)
         self.log_feat = partial(self.log_to_table, self.log_feat_table)
         self.log_data = partial(self.log_to_table, self.log_data_table)
         self.log_results = partial(self.log_to_table, self.log_results_table)
 
-    def __post_init__(self):
+    def __post_init__(self) -> None:
+        """Initializes the Logger object."""
         self.cv_results = chkenv("CV_RESULTS")
         ptab = f"params_{self.model_type}"
         if self.cv_results == "ALL":
@@ -64,7 +72,8 @@ class Logger:
         self,
         log_table: str,
         _dict: dict,
-    ):
+    ) -> None:
+        """Sends a dictionary to a database table."""
         cvisall = self.cv_results == "ALL"
         if cvisall and ("param" in log_table or "result" in log_table):
[…]

### 2024-02-04 src/main.py

@@ -1,8 +1,8 @@
+"""A module to run all models in the database."""
 from random import choice
 
 from tqdm import tqdm
 
-# local imports
 from alexlib.db.managers import PostgresManager
 from alexlib.core import chkenv
 from alexlib.iters import list_gen
@@ -29,7 +29,8 @@ feat_dict = {
 feat_list = list(feat_dict.values())
 
 
-def rand_feat():
+def rand_feat() -> list:
+    """Returns a random feature from the feat_list. If random_state is False, returns the entire list."""
     return [choice(feat_list)] if random_state else feat_list
 
 
@@ -38,6 +39,7 @@ def run_all_models(
     reset_schema: bool = reset_schema,
     cnxn: PostgresManager = cnxn,
 ) -> bool:
+    """Runs all models in the database. If reset_schema is True, resets the schema. If random_state is False, runs all models. If random_state is True, runs a random model. If grouped is True, runs all models with the same feature. If grouped is False, runs all models with all features. If inf is True, runs the models infinitely. If inf is False, runs the models once."""
     if reset_schema:
         cnxn.drop_table_pattern("results")
         cnxn.drop_table_pattern("param")
@@ -60,7 +62,8 @@ def run_all_models(
             return True
 
 
-def try_except_pass(func, *args, **kwargs):
+def try_except_pass(func, *args, **kwargs) -> None:
+    """Runs a function and passes if a RuntimeError is raised."""
     try:
         func(*args, **kwargs)
     except RuntimeError:

### 2024-10-19 src/model/analysis.py
refactor deps

@@ -3,8 +3,10 @@
 from collections.abc import Generator
 from dataclasses import dataclass, field
 from datetime import datetime
+from itertools import chain
 
 from baycomp import two_on_multiple
+from duckdb import DuckDBPyConnection
 from matplotlib.colors import BoundaryNorm, ListedColormap
 from matplotlib.pyplot import legend, subplots, tick_params, title, xlabel, ylabel
 from numpy import array, bool_, float_, int_, isnan, nan, zeros
@@ -18,10 +20,23 @@ from tqdm import tqdm
 from alexlib.core import chkenv
 from alexlib.db.managers import PostgresManager
 from alexlib.df import filter_df, get_distinct_col_vals
-from alexlib.iters import get_comb_gen, get_idx_val, link
+from alexlib.iters import get_comb_gen
 from alexlib.maths import combine_domains, get_list_difs, get_rect_area
-from utils import db_mgr
-from utils.constants import LEFT, MID, OUT, RIGHT, ROPE, WINDOWPANE_PLOT_PARAMS
+
+from utils import get_idx_val
+from utils.constants import (
+    CV_NREPEATS,
+    EVAL_ROPE,
+    LEFT,
+    LOG_SCHEMA,
+    MID,
+    OUT,
+    RIGHT,
+    ROPE,
+    ROPE_FLEXIBLE,
+    ROPE_UPBOUND,
+    WINDOWPANE_PLOT_PARAMS,
+)
 
 
 class Abroca:
@@ -375,10 +390,10 @@ class ModelResult:
 class Results:
     """A class for the model results."""
 
-    schema: str = field(default=chkenv("LOG_SCHEMA"))
-    table: str = field(default="v_all_runs_results")
-    rope: float = field(default=chkenv("EVAL_ROPE", astype=float))
-    runs: int = field(default=chkenv("CV_NREPEATS", astype=int))
+    schema: str = LOG_SCHEMA
+    table: str = "v_all_runs_results"
+    rope: float = EVAL_ROPE
+    runs: int = CV_NREPEATS
     lim: int = field(default=None)
     obj_list: list = field(default_factory=list)
 
@@ -398,8 +413,8 @@ class Results:
     @staticmethod
     def rope_eval(
         outcome: tuple,
-        flexible: bool = chkenv("ROPE_FLEXIBLE", astype=bool),
-        upbound: float = chkenv("ROPE_UPBOUND", astype=float),
[…]

### 2024-10-19 src/model/engine.py

@@ -12,55 +12,34 @@ of the class.
 from functools import cached_property
 from warnings import catch_warnings
 
-from analysis import RocCurve
-from features import Features
-from logger import Logger
 from numpy import array
 from pandas import DataFrame, Series
-from params import Params, overwrite_std_params
-from preprocessing import DataPrep
-from setup import random_state
 from sklearn.decomposition import PCA
 from sklearn.feature_selection import VarianceThreshold
 from sklearn.metrics import classification_report, confusion_matrix
 from sklearn.model_selection import GridSearchCV, RepeatedStratifiedKFold
 from sklearn.pipeline import Pipeline
 
-from alexlib.core import chkenv
+from model.analysis import RocCurve
+from model.features import Features
+from model.logger import Logger
+from model.params import Params, overwrite_std_params
+from model.preprocessing import DataPrep
+from utils.constants import (
+    CV_NREPEATS,
+    CV_NSPLITS,
+    CV_REFIT,
+    CV_VERBOSE,
+    NROWS,
+    RANDOM_STATE,
+    SEARCH_RANDOM,
+    SIMPLE_NUM_IMPUTE,
+    TEST_SIZE,
+)
 
 
 class ModelEngine:
     """A class to fit, test, and log the results of a machine learning model."""
-
-    @property
-    def n_splits(self) -> int:
-        """The number of splits to use in the cross-validation."""
-        return chkenv("CV_NSPLITS", type=int)
-
-    @property
-    def n_repeats(self) -> int:
-        """The number of repeats to use in the cross-validation."""
-        return chkenv("CV_NREPEATS", type=int)
-
-    @property
-    def reduce_dim(self) -> bool:
-        """Whether to reduce the dimensions of the data before fitting the model."""
-        return chkenv("REDUCE_DIM", type=bool)
-
-    @property
-    def verbose(self) -> int:
-        """The verbosity level of the model fitting."""
-        return chkenv("CV_VERBOSE", type=int)
-
-    @property
-    def simple_num_impute(self) -> bool:
-        """Whether to use simple imputation for numerical data."""
-        return chkenv("SIMPLE_NUM_IMPUTE", type=bool)
-
-    @property
-    def search_random(self) -> bool:
-        """Whether to use random search for hyperparameter optimization."""
-        return chkenv("SEARCH_RANDOM", type=bool)
 
     @cached_property
     def params(self) -> Params:
@@ -76,7 +55,7 @@ class ModelEngine:
     def crossval(self) -> RepeatedStratifiedKFold:
[…]

### 2024-10-19 src/model/features.py

@@ -1,11 +1,40 @@
+from dataclasses import dataclass, field
+from functools import cached_property
 from itertools import chain
 
 from pandas import DataFrame
 
-from alexlib.core import chkenv
 from alexlib.df import filter_df
 from alexlib.iters import rm_pattern
-from utils.db_helpers import Table
+
+from utils.constants import (
+    USE_ACADEMIC,
+    USE_ALL,
+    USE_BY_ACTIVITY,
+    USE_DEMOGRAPHIC,
+    USE_ENGAGEMENT,
+    USE_IDS,
+    USE_MOMENTS,
+    USE_TEXT,
+)
+
+CATEGORY_COLUMNS = (
+    "course_id",
+    "module_id",
+    "presentation_id",
+)
+TO_DROP_COLUMNS = ("student_id", "unreg_date", "reg_date_dif")
+FINAL_RESULT_COLUMNS = (
+    "final_result",
+    "final_result_id",
+    "is_pass_or_distinction",
+    "is_distinction",
+    "is_pass",
+    "is_fail",
+    "is_withdrawn",
+    "is_withdraw_or_fail",
+)
+SPLIT_COLUMNS = ("is_stem", "is_female", "has_disability")
 
 
 def wo_ids(x: str) -> str:
@@ -13,29 +42,20 @@ def wo_ids(x: str) -> str:
     return rm_pattern(x, "_id")
 
 
+@dataclass
 class Features:
     """A class to describe the features in a database table. Inherits from the ProjectTable class in the alexlib.db.objects module."""
 
-    cat_cols = [
-        "course_id",
-        "module_id",
-        "presentation_id",
-    ]
-    to_drop_cols = ["student_id", "unreg_date", "reg_date_dif"]
-    final_result_cols = [
-        "final_result",
-        "final_result_id",
-        "is_pass_or_distinction",
-        "is_distinction",
-        "is_pass",
-        "is_fail",
-        "is_withdrawn",
-        "is_withdraw_or_fail",
-    ]
+    df: DataFrame
+    schema: str = "eval"
+    table: str = "v_features"
+    field_col: str = "column_name"
+    to_include: list[str] = field(default_factory=list)
+    to_exclude: list[str] = field(default_factory=list)
 
-    def get_col_names(self, df: DataFrame) -> list:
+    def get_col_names(self) -> list:
         """Returns a list of column names from a DataFrame."""
-        return df.loc[:, self.field_col]
+        return self.df.loc[:, self.field_col].tolist()
 
[…]

### 2024-10-19 src/model/logger.py

@@ -1,12 +1,11 @@
 from dataclasses import dataclass, field
-from datetime import datetime as dt
+from datetime import datetime
 from functools import partial
 
 from duckdb import DuckDBPyConnection
 from pandas import DataFrame
 
-from alexlib.core import chkenv
-
+from utils.constants import CV_RESULTS, LOG_SCHEMA
 from utils.elt_config import get_cnxn
 
 
@@ -16,7 +15,7 @@ class Logger:
 
     model_type: str
     cnxn: DuckDBPyConnection = field(default_factory=get_cnxn)
-    log_schema: str = field(default=chkenv("LOG_SCHEMA"))
+    log_schema: str = LOG_SCHEMA
     log_runs_table: str = field(default="runs")
     log_runs_id_col: str = field(default="id")
     log_id_col: str = field(default="run_id")
@@ -55,7 +54,7 @@ class Logger:
 
     def __post_init__(self) -> None:
         """Initializes the Logger object."""
-        self.cv_results = chkenv("CV_RESULTS")
+        self.cv_results = CV_RESULTS
         ptab = f"params_{self.model_type}"
         if self.cv_results == "ALL":
             self.log_results_table = self.log_results_table + "_all"
@@ -88,12 +87,15 @@ class Logger:
             index=False,
         )
 
-    def log_run(self, _keys: list = None) -> None:
+    @property
+    def log_record(self) -> dict:
+        """Returns the log record for the Logger object."""
+        return {
+            "run_id": self.run_id,
+            "model_type": self.model_type,
+            "timestamp": datetime.now(),
+        }
+
+    def log_run(self) -> None:
         """Logs a run to the runs table."""
-        if _keys is None:
-            _keys = ["id", "model_type", "timestamp"]
-        now: dt = (dt.now(),)
-        vals = [self.run_id, self.model_type, now]
-        _range = range(len(_keys))
-        _dict = {_keys[i]: vals[i] for i in _range}
-        self.send_log(self.log_runs_table, _dict)
+        self.send_log(self.log_runs_table, self.log_record)

### 2024-10-19 src/model/main.py

@@ -1,62 +1,47 @@
-from os import getenv
-
 from numpy.random import choice
 from tqdm import tqdm
 
-from alexlib.core import istrue
-from alexlib.files.utils import path_search
 from model.engine import ModelEngine
-from model.features import Features
+from model.features import SPLIT_COLUMNS, Features
 from model.params import Params
-from utils.constants import MODEL_TYPES
-from utils.db_helpers import DbHelper
-from utils.utils import list_gen
-
-split_cols = ["is_stem", "is_female", "has_disability"]
-search_int = int(getenv("SEARCH_ITER"))
-grouped = istrue(getenv("SEARCH_GROUPED"))
-rand = istrue(getenv("SEARCH_RANDOM"))
-inf = istrue(getenv("INF_ITER"))
-schema = getenv("LOG_SCHEMA")
-reset_schema = istrue(getenv("RESET_SCHEMA"))
+from utils.constants import INF_ITER, MODEL_TYPES, SEARCH_GROUPED, SEARCH_RANDOM
 
 feat_dict = {
-    "demographic": Features(to_include=split_cols, use_demographic=True),
-    "engagement": Features(to_include=split_cols, use_engagement=True),
-    "academic": Features(to_include=split_cols, use_academic=True),
-    "all": Features(to_include=split_cols, use_all=True),
+    "demographic": Features(to_include=SPLIT_COLUMNS, use_demographic=True),
+    "engagement": Features(to_include=SPLIT_COLUMNS, use_engagement=True),
+    "academic": Features(to_include=SPLIT_COLUMNS, use_academic=True),
+    "all": Features(to_include=SPLIT_COLUMNS, use_all=True),
 }
 feat_list = list(feat_dict.values())
 
 
 def rand_feat():
-    return [choice(feat_list)] if rand else feat_list
+    return [choice(feat_list)] if SEARCH_RANDOM else feat_list
 
 
-def drop_tab_pattern(
-    dbh: DbHelper,
-    pattern: str,
-    schema: str = schema,
-    cascade: bool = True,
-):
-    tabs = dbh.get_all_schema_tables(schema)
-    droptabs = [x for x in tabs if pattern in x]
-    for tab in droptabs:
-        dbh.drop_table(schema, tab, cascade=cascade)
+# redo how logs work
+# log to files instead of db
 
 
-def run_all_models(schema: str, reset_schema: bool, dbh: DbHelper):
-    if reset_schema:
[…]

### 2024-10-19 src/model/params.py

@@ -19,8 +19,8 @@ from sklearn.tree import DecisionTreeClassifier
 
 from alexlib.core import chkenv
 from alexlib.maths import discrete_exp_dist
-from utils import JOB_CORES, NROWS, RANDOM_STATE
-from utils.constants import MODEL_TYPES
+
+from utils.constants import JOB_CORES, MODEL_TYPES, NROWS, RANDOM_STATE
 
 MODEL_TYPE_MAP = {
     "logreg": LogisticRegression,

### 2024-10-19 src/model/preprocessing.py

@@ -12,6 +12,7 @@ from sklearn.preprocessing import OneHotEncoder, StandardScaler
 
 from alexlib.core import chkenv
 from alexlib.df import filter_df
+
 from model.features import Features
 from utils.db_helpers import Table
 

### 2024-10-19 src/utils/constants.py

@@ -31,6 +31,9 @@ MODEL_TYPES = (
     # "compnb",
     # "gauss",
 )
+# logs
+LOG_SCHEMA = "model"
+(LOG_PATH := PROJECT_PATH / "logs").mkdir(exist_ok=True)
 
 # model search
 INF_ITER = False

### 2024-10-19 tests/test_model.py

@@ -1,0 +1,8 @@
+from pytest import fixture
+
+from model.features import Features
+
+
+@fixture(scope="module")
+def features():
+    return Features()

### 2024-10-19 src/model/preprocessing.py
fix student grades

@@ -10,46 +10,26 @@ from sklearn.model_selection import train_test_split
 from sklearn.pipeline import Pipeline
 from sklearn.preprocessing import OneHotEncoder, StandardScaler
 
-from alexlib.core import chkenv
 from alexlib.df import filter_df
 
 from model.features import Features
-from utils.db_helpers import Table
+from utils.constants import (
+    PREDICT_COL,
+    RANDOM_STATE,
+    SIMPLE_NUM_IMPUTE,
+    TEST_SIZE,
+)
 
 
 @dataclass
 class DataPrep:
     """A class to preprocess data for machine learning."""
 
-    feat: Features = field()
+    data: DataFrame
+    features: Features
     schema: str = field(default="first30")
     table: str = field(default="all_features")
     df_filter: tuple = field(default=None)
-
-    @property
-    def context(self) -> str:
-        """Returns the context."""
-        return chkenv("CONTEXT")
-
-    @property
-    def nrows(self) -> int:
-        """Returns the number of rows to retrieve from the database."""
-        return chkenv("NROWS", type=int)
-
-    @property
-    def test_size(self) -> float:
-        """Returns the test size for the train_test_split function."""
-        return chkenv("TEST_SIZE", type=float)
-
-    @property
-    def random_state(self) -> int:
-        """Returns the random state for the train_test_split function."""
-        return chkenv("RANDOM_STATE", type=int)
-
-    @property
-    def simple_num_impute(self) -> bool:
-        """Returns whether to use the simple imputer for numeric columns."""
-        return chkenv("SIMPLE_NUM_IMPUTE", type=bool)
 
     def __post_init__(self) -> None:
         """Initializes the DataPrep object."""
@@ -62,7 +42,10 @@ class DataPrep:
         ]
     )
     knn_num_trans = Pipeline(
-        [("knn_num_imputer", KNNImputer()), ("scaler", StandardScaler())]
+        [
+            ("knn_num_imputer", KNNImputer()),
+            ("scaler", StandardScaler()),
+        ]
     )
     simp_num_trans = Pipeline(
         [
@@ -74,30 +57,25 @@ class DataPrep:
         [("bool_imputer", SimpleImputer(strategy="constant", fill_value=0))]
     )
 
-    def get_data(self) -> DataFrame:
-        """Returns the dataframe from the database."""
-        self.data = Table(self.context, self.schema, self.table, nrows=self.nrows)
-        return self.data.df
-
[…]

### 2024-10-19 src/utils/elt_config.py

@@ -417,3 +417,4 @@ if __name__ == "__main__":
     """
     print("Sources Without Targets:", sorted(qdir.sources_without_targets))
     print("Targets Without Sources:", sorted(qdir.targets_without_sources))
+    main()

### 2024-10-19 tests/test_model.py

@@ -1,8 +1,34 @@
+from duckdb import DuckDBPyConnection
+from pandas import DataFrame
 from pytest import fixture
 
 from model.features import Features
+from model.preprocessing import DataPrep
+
+SCHEMA = "first30"
+TABLE = "all_features"
+
+
+@fixture(scope="module")
+def schema():
+    return SCHEMA
+
+
+@fixture(scope="module")
+def table():
+    return TABLE
+
+
+@fixture(scope="module")
+def data(schema: str, table: str, cnxn: DuckDBPyConnection):
+    return cnxn.sql(f"select * from {schema}.{table}").df()
 
 
 @fixture(scope="module")
 def features():
     return Features()
+
+
+@fixture(scope="module")
+def dataprep(data: DataFrame, features: Features):
+    return DataPrep(data, features)

### 2024-10-20 src/orm/model.py
update create model tables sql

@@ -14,9 +14,14 @@ class ModelTable:
         return f"{self.__schema__}.{self.__tablename__}"
 
 
+class ModelTypes(Base, ModelTable):
+    __tablename__ = "types"
+    model_type = Column(String(45))
+
+
 class ModelRuns(Base, ModelTable):
     __tablename__ = "runs"
-    model_type = Column(String(45))
+    model_type_id = Column(String(45))
     model_params = Column(JSON)
     timestamp = Column(DateTime)
 

### 2024-10-20 src/utils/elt_config.py

@@ -25,19 +25,38 @@ SQL_BLACKLIST = (
     "INSERT",
     "INTO",
 )
-CREATE_MODEL_RUNS_TABLE = """
-create table model.runs (
-    id serial primary key,
-    model_type text not null,
-    timestamp timestamp not null
-)
-"""
 CREATE_MODEL_TYPES_TABLE = """
 create table model.types(
 id serial primary key,
 model_type text not null
 );
 """
+CREATE_MODEL_RUNS_TABLE = """
+create table model.runs (
+    id serial primary key,
+    model_type_id integer not null,
+    model_params json not null,
+    timestamp timestamp not null
+)
+"""
+CREATE_MODEL_RESULTS_TABLE = """
+create table model.results(
+id serial primary key,
+run_id integer not null,
+mean_fit_time float not null,
+std_fit_time float not null,
+mean_score_time float not null,
+std_score_time float not null,
+mean_test_roc_auc float not null,
+std_test_roc_auc float not null,
+rank_test_roc_auc integer not null
+);
+"""
+CREATE_MODEL_TABLES = (
+    CREATE_MODEL_RUNS_TABLE,
+    CREATE_MODEL_TYPES_TABLE,
+    CREATE_MODEL_RESULTS_TABLE,
+)
 SOURCE_TABLES = {
     "MODEL_RUNS",
     "MODEL_TYPES",
@@ -369,6 +388,10 @@ def main(
     cnxn = get_cnxn()
     timer.log_from_last("Connection & schemas")
     create_all_schemas(cnxn)
+
+    # Create model tables
+    for sql in CREATE_MODEL_TABLES:
+        cnxn.execute(sql)
 
     # Load landing data
     data_dir = DataDirectory()

### 2024-10-20 src/utils/constants.py
finish analysis schema updates

@@ -15,7 +15,7 @@ DATA_PATH = PROJECT_PATH / "data"
 RAW_PATH = DATA_PATH / "raw"
 CSV_PATHS = list(RAW_PATH.glob("*.csv"))
 DB_PATH = DATA_PATH / "learning.db"
-SCHEMAS = ("landing", "main", "agg", "model", "eval", "feat", "first30")
+SCHEMAS = ("landing", "main", "agg", "model", "eval", "feat", "first30", "analysis")
 
 QUERY_PATH = SOURCE_PATH / "queries"
 MODEL_TYPES = (

### 2024-10-20 src/utils/elt_config.py

@@ -26,36 +26,76 @@ SQL_BLACKLIST = (
     "INTO",
 )
 CREATE_MODEL_TYPES_TABLE = """
-create table model.types(
-id serial primary key,
+create or replace table model.types(
+id integer primary key,
 model_type text not null
 );
 """
 CREATE_MODEL_RUNS_TABLE = """
-create table model.runs (
-    id serial primary key,
+create or replace table model.runs (
+    id integer primary key,
+    iter_id integer not null,
     model_type_id integer not null,
     model_params json not null,
     timestamp timestamp not null
 )
 """
 CREATE_MODEL_RESULTS_TABLE = """
-create table model.results(
-id serial primary key,
+create or replace table model.results(
+id integer primary key,
 run_id integer not null,
+iter_id integer not null,
 mean_fit_time float not null,
 std_fit_time float not null,
 mean_score_time float not null,
 std_score_time float not null,
 mean_test_roc_auc float not null,
 std_test_roc_auc float not null,
-rank_test_roc_auc integer not null
+rank_test_roc_auc integer not null,
+mean_test_accuracy float not null,
+std_test_accuracy float not null
 );
 """
-CREATE_MODEL_TABLES = (
+CREATE_MODEL_FEATURES_TABLE = """
+create or replace table model.features(
+id integer primary key,
+run_id integer not null,
+to_predict_column text not null,
+use_academic boolean not null,
+use_demographic boolean not null,
+use_engagement boolean not null,
+use_moments boolean not null,
+use_ids boolean not null,
+use_text boolean not null,
+use_by_activity boolean not null
+);
+"""
+CREATE_MODEL_WARNINGS_TABLE = """
+create or replace table model.warnings(
+id integer primary key,
+run_id integer not null,
+warnings text not null
+);
+"""
+CREATE_ANALYSIS_ABROCA_TABLE = """
+create or replace table analysis.abroca(
+index integer primary key,
+run_id integer not null,
+iter_id integer not null,
+course_id integer not null,
+is_stem boolean not null,
+is_female boolean not null,
+has_disability boolean not null
+);
+"""
+
+CREATE_TABLES = (
     CREATE_MODEL_RUNS_TABLE,
     CREATE_MODEL_TYPES_TABLE,
     CREATE_MODEL_RESULTS_TABLE,
+    CREATE_MODEL_FEATURES_TABLE,
[…]

### 2024-10-20 src/utils/elt_config.py
single quotes in f string

@@ -453,7 +453,7 @@ def main(
             schema, table_name, query_path.read_text(), orreplace=replace
         )
         print(
-            f"Creating {schema}.{table_name} from {"/".join(query_path.parts[-3:])}",
+            f"Creating {schema}.{table_name} from {'/'.join(query_path.parts[-3:])}",
             end="... ",
         )
         cnxn.execute(sql)

### 2024-10-20 tests/conftest.py
update test db to memory

@@ -7,7 +7,6 @@ from utils.constants import (
     BLUE,
     CSV_PATHS,
     DATA_PATH,
-    DB_PATH,
     FIGURES_PATH,
     GRAY,
     HOME,
@@ -40,7 +39,7 @@ from utils.elt_config import (
 
 @fixture(scope="session")
 def cnxn() -> DuckDBPyConnection:
-    cnxn = get_cnxn(database=DB_PATH)
+    cnxn = get_cnxn(database=":memory:")
     return cnxn
 
 

### 2024-10-20 src/utils/constants.py
add export path to constants

@@ -11,8 +11,9 @@ PROJECT_PATH = SOURCE_PATH.parent
 DOTENV_PATH = PROJECT_PATH / ".env"
 
 FIGURES_PATH = PROJECT_PATH / "figures"
-DATA_PATH = PROJECT_PATH / "data"
-RAW_PATH = DATA_PATH / "raw"
+(DATA_PATH := PROJECT_PATH / "data").mkdir(exist_ok=True)
+(RAW_PATH := DATA_PATH / "raw").mkdir(exist_ok=True)
+(EXPORT_PATH := DATA_PATH / "export").mkdir(exist_ok=True)
 CSV_PATHS = list(RAW_PATH.glob("*.csv"))
 DB_PATH = DATA_PATH / "learning.db"
 SCHEMAS = ("landing", "main", "agg", "model", "eval", "feat", "first30", "analysis")

### 2024-10-20 src/utils/constants.py
add dataset download

@@ -10,11 +10,15 @@ SOURCE_PATH = Path(__file__).parent.parent
 PROJECT_PATH = SOURCE_PATH.parent
 DOTENV_PATH = PROJECT_PATH / ".env"
 
+OULAD_BASE = "https://analyse.kmi.open.ac.uk"
+OULAD_URL = f"{OULAD_BASE}/open_dataset/download"
+OULAD_MD5_URL = f"{OULAD_BASE}/open_dataset/downloadCheckSum"
+OULAD_MD5 = "7412686fd77cf0e0ee1e8c3e9b354308"
+
 FIGURES_PATH = PROJECT_PATH / "figures"
 (DATA_PATH := PROJECT_PATH / "data").mkdir(exist_ok=True)
 (RAW_PATH := DATA_PATH / "raw").mkdir(exist_ok=True)
 (EXPORT_PATH := DATA_PATH / "export").mkdir(exist_ok=True)
-CSV_PATHS = list(RAW_PATH.glob("*.csv"))
 DB_PATH = DATA_PATH / "learning.db"
 SCHEMAS = ("landing", "main", "agg", "model", "eval", "feat", "first30", "analysis")
 

### 2024-10-20 src/utils/elt_config.py

@@ -111,6 +111,11 @@ SOURCE_TABLES = {
 }
 
 
+def get_csv_paths(parent_path: Path = RAW_PATH) -> list[Path]:
+    """Return a list of CSV paths."""
+    return list(parent_path.glob("*.csv"))
+
+
 def get_cnxn(database: Path = DB_PATH, read_only: bool = False) -> DuckDBPyConnection:
     return connect(database=database, read_only=read_only)
 

### 2024-10-20 src/utils/get_dataset.py

@@ -1,0 +1,78 @@
+from functools import partial
+from hashlib import md5
+from logging import getLogger
+from pathlib import Path
+from zipfile import ZipFile
+
+from requests import get
+
+from utils.constants import OULAD_MD5_URL, OULAD_URL, RAW_PATH
+from utils.elt_config import get_csv_paths
+
+logger = getLogger(__name__)
+SOURCE_TABLE_MAP = {
+    "assessments": "assessments",
+    "courses": "courses",
+    "studentAssessment": "student_assessment",
+    "studentInfo": "student_info",
+    "studentRegistration": "student_registration",
+    "studentVle": "student_vle",
+    "vle": "vle",
+}
+DATASET_PATH = RAW_PATH / "dataset.zip"
+CHECKSUM_PATH = RAW_PATH / "dataset.md5"
+EXTRACT_PATH = RAW_PATH
+
+
+def download_file(url: str, path: Path) -> None:
+    """Download a file."""
+    logger.info(f"Downloading dataset from {url} to {path}.")
+    with get(url, stream=True) as response:
+        response.raise_for_status()
+        with path.open("wb") as file:
+            for chunk in response.iter_content(chunk_size=8192):
+                file.write(chunk)
+    logger.info(f"Downloaded dataset to {path}.")
+
+
+download_dataset = partial(download_file, OULAD_URL, DATASET_PATH)
+download_checksum = partial(download_file, OULAD_MD5_URL, CHECKSUM_PATH)
+
+
+def validate_checksum(file_path: Path, checksum_path: Path = CHECKSUM_PATH) -> bool:
+    """Validate the checksum of a file."""
+    logger.info(f"Validating checksum of {file_path}.")
+    with file_path.open("rb") as file:
+        checksum = md5(file.read()).hexdigest()
+    expected = checksum_path.read_bytes().decode().strip()
+    if checksum != expected:
+        logger.error(f"Checksum mismatch: {checksum} != {expected}.")
+        return False
+    logger.info(f"Checksum validated: {checksum} == {expected}.")
+    return True
+
+
+def unzip_file(zip_path: Path, extract_path: Path = EXTRACT_PATH) -> None:
+    """Unzip a file."""
+    logger.info(f"Unzipping {zip_path} to {extract_path}.")
+    with ZipFile(zip_path, "r") as file:
+        file.extractall(extract_path)
[…]

### 2024-10-20 tests/conftest.py

@@ -5,7 +5,6 @@ from pytest import FixtureRequest, fixture
 
 from utils.constants import (
     BLUE,
-    CSV_PATHS,
     DATA_PATH,
     FIGURES_PATH,
     GRAY,
@@ -33,6 +32,7 @@ from utils.elt_config import (
     QueriesDirectory,
     create_all_schemas,
     get_cnxn,
+    get_csv_paths,
     load_landing_data,
 )
 
@@ -75,7 +75,7 @@ def cnxn_with_landing_data(
         QUERY_PATH,
         FIGURES_PATH,
     )
-    + tuple(CSV_PATHS),
+    + tuple(get_csv_paths()),
 )
 def constant_path(request: FixtureRequest) -> Path:
     return request.param

### 2024-10-20 tests/test_elt_config.py

@@ -7,7 +7,6 @@ from pytest import FixtureRequest, fixture
 from alexlib.files import Directory, File
 
 from orm import SCHEMAS
-from utils.constants import CSV_PATHS
 from utils.elt_config import (
     SQL_BLACKLIST,
     DataDirectory,
@@ -17,6 +16,7 @@ from utils.elt_config import (
     get_all_schemas,
     get_all_table_names,
     get_create_object_command,
+    get_csv_paths,
     get_info_schema_df,
     get_object_type,
     get_schema_table_name,
@@ -29,7 +29,7 @@ def schema(request: FixtureRequest) -> str:
     return request.param
 
 
-@fixture(scope="module", params=CSV_PATHS)
+@fixture(scope="module", params=get_csv_paths())
 def csv_path(request: FixtureRequest) -> Path:
     return request.param
 

### 2024-10-20 src/utils/get_dataset.py
add get data as actions step

@@ -7,7 +7,6 @@ from zipfile import ZipFile
 from requests import get
 
 from utils.constants import OULAD_MD5_URL, OULAD_URL, RAW_PATH
-from utils.elt_config import get_csv_paths
 
 logger = getLogger(__name__)
 SOURCE_TABLE_MAP = {
@@ -60,7 +59,7 @@ def unzip_file(zip_path: Path, extract_path: Path = EXTRACT_PATH) -> None:
     logger.info(f"Unzipped {zip_path} to {extract_path}.")
 
 
-def get_dataset() -> None:
+def main() -> None:
     """Download and extract the dataset."""
     if not DATASET_PATH.exists():
         download_dataset()
@@ -74,5 +73,5 @@ def get_dataset() -> None:
         (EXTRACT_PATH / f"{orig}.csv").rename(RAW_PATH / f"{dest}.csv")
 
 
-if len(get_csv_paths()) == 0:
-    get_dataset()
+if __name__ == "__main__":
+    main()

### 2024-10-21 paper/paper.tex

@@
                 Final Outcomes
-                LAnding to Main Database schema decisions
+                Landing to Main Database schema decisions
                 Main to First30 Database schema decisions

### 2024-10-21 src/model/analysis.py
add analysis tests

@@ -3,13 +3,14 @@
 from collections.abc import Generator
 from dataclasses import dataclass, field
 from datetime import datetime
+from functools import cached_property
 from itertools import chain
 
 from baycomp import two_on_multiple
 from duckdb import DuckDBPyConnection
 from matplotlib.colors import BoundaryNorm, ListedColormap
 from matplotlib.pyplot import legend, subplots, tick_params, title, xlabel, ylabel
-from numpy import array, bool_, float_, int_, isnan, nan, zeros
+from numpy import array, bool_, floating, int_, integer, isnan, nan, ndarray, zeros
 from pandas import DataFrame, Series
 from scikit_posthocs import posthoc_nemenyi_friedman
 from scipy.stats import friedmanchisquare
@@ -17,7 +18,6 @@ from seaborn import heatmap
 from sklearn.metrics import roc_auc_score, roc_curve
 from tqdm import tqdm
 
-from alexlib.core import chkenv
 from alexlib.db.managers import PostgresManager
 from alexlib.df import filter_df, get_distinct_col_vals
 from alexlib.iters import get_comb_gen
@@ -25,6 +25,7 @@ from alexlib.maths import combine_domains, get_list_difs, get_rect_area
 
 from utils import get_idx_val
 from utils.constants import (
+    ALPHA,
     CV_NREPEATS,
     EVAL_ROPE,
     LEFT,
@@ -109,8 +110,9 @@ class Abroca:
     def __init__(self, split_col: str, curve_dict: dict) -> None:
         """Initialize the class."""
         self.split_col = split_col
-        self.roc1 = curve_dict[self.keys[0]]
-        self.roc2 = curve_dict[self.keys[-1]]
+        self.curves = curve_dict  # Add this line
+        self.roc1 = self.curves[self.keys[0]]
+        self.roc2 = self.curves[self.keys[-1]]
         self.steps()
 
     @staticmethod
@@ -156,42 +158,33 @@ class Abroca:
             return ax
 
 
+@dataclass
 class RocCurve:
     """A class for calculating the ROC curve."""
 
-    def get_rates(self) -> tuple[list, list]:
-        """Get the rates for the ROC curve."""
-        fpr, tpr, _ = roc_curve(self.y_true, self.y_prob)
-        return fpr, tpr
+    y_true: ndarray
+    y_prob: ndarray
+    X_test: ndarray
+    fpr: ndarray = field(init=False)
[…]

### 2024-10-21 tests/test_model_analysis.py

@@ -1,0 +1,381 @@
+# test_analysis.py
+
+from numpy import array, inf
+from numpy.testing import assert_array_equal
+from pandas import DataFrame, Timestamp
+from pytest import fixture, mark
+
+from model.analysis import (
+    Abroca,
+    ModelResult,
+    Results,
+    RocCurve,
+    format_clf_params,
+    get_num,
+    try_array_float_list,
+)
+
+
+# Fixtures for sample data used across multiple tests
+@fixture
+def sample_arrays():
+    return {
+        "float_array": array([1.0, 2.0, 3.0]),
+        "int_array": array([1, 2, 3]),
+        "str_num_array": array(["1", "2", "3"]),
+        "str_alpha_array": array(["a", "b", "c"]),
+        "bool_array": array([True, False, True]),
+        "zero_one_array": array([0, 1, 0]),
+    }
+
+
+@fixture
+def sample_series():
+    data = {
+        "param1": array([1, 2, 3]),
+        "param2": array([0.1, 0.2, 0.3]),
+        "param3_id": array([100, 101, 102]),
+        "n_jobs": array([1, 2, 3]),
+        "warm_start": array([1, 0, 1]),
+    }
+    return DataFrame(data)
+
+
+@fixture
+def sample_y_true():
+    return [0, 0, 1, 1]
+
+
+@fixture
+def sample_y_prob():
+    return [0.1, 0.4, 0.35, 0.8]
+
+
+@fixture
+def sample_y_true_2():
+    return [0, 1, 0, 1]
+
+
+@fixture
+def sample_y_prob_2():
+    return [0.2, 0.3, 0.6, 0.7]
+
+
+@fixture
+def sample_X_test():
+    return DataFrame({"test_split": [0, 0, 1, 1]})
+
+
+# Parameterized tests for get_num function
+@mark.parametrize(
+    "input_str, expected_output",
+    [
+        ("123", 123),
+        ("123.456", 123.456),
+        ("abc", "abc"),
+        (None, None),
+        ("1e3", 1000.0),
+        ("inf", inf),
+        ("-inf", -inf),
+    ],
+)
+def test_get_num(input_str, expected_output):
+    """Test the get_num function with various inputs."""
+    assert get_num(input_str) == expected_output
+
+
+# Parameterized tests for try_array_float_list function
+@mark.parametrize(
+    "array_name, key, expected_result",
+    [
+        ("float_array", "param", [1.0, 2.0, 3.0]),
+        ("str_num_array", "param", [1, 2, 3]),
[…]

### 2024-10-21 tests/test_model_analysis.py
re-export png for rope figure

@@ -32,11 +32,11 @@ def sample_arrays():
 @fixture
 def sample_series():
     data = {
-        "param1": array([1, 2, 3]),
-        "param2": array([0.1, 0.2, 0.3]),
-        "param3_id": array([100, 101, 102]),
-        "n_jobs": array([1, 2, 3]),
-        "warm_start": array([1, 0, 1]),
+        "param1": [1, 2, 3],
+        "param2": [0.1, 0.2, 0.3],
+        "param3_id": [100, 101, 102],
+        "n_jobs": [1, 2, 3],
+        "warm_start": [1, 0, 1],
     }
     return DataFrame(data)
 

### 2024-10-23 src/utils/elt_config.py
add build figures and elt as script

@@ -469,20 +469,3 @@ def main(
     cnxn.execute(f"""EXPORT DATABASE '{str(data_dir.export_path)}' (FORMAT PARQUET)""")
     timer.log_from_last("Export database")
     cnxn.close()
-
-
-if __name__ == "__main__":
-    # main()
-    qdir = QueriesDirectory()
-    """
-    for path, sources in qdir.path_source_map.items():
-        print("/".join(path.parts[-3:]), "\n\t" + "\n\t".join(sources))
-        print(qdir.path_normalized_name_map[path])
-        break
-    print(qdir.target_source_df)
-    print(qdir.source_ntargets_map)
-    print(qdir.target_nsources_map, "\n")
-    """
-    print("Sources Without Targets:", sorted(qdir.sources_without_targets))
-    print("Targets Without Sources:", sorted(qdir.targets_without_sources))
-    main()

### 2024-10-23 src/utils/elt_config.py
rm duplicate and wrong agg_course_details

@@ -447,7 +447,7 @@ def main(
     # Load non-landing data
     for query_path in tqdm(queries.get_sorted_nonlanding_query_paths()):
         if query_path.stem.startswith("_"):
-            print(f"skipping {query_path.relative_to(queries.path)}")
+            logger.info(f"skipping {query_path.relative_to(queries.path)}")
             continue
         if check_sql_path_for_blacklist(query_path):
             raise ValueError(f"Blacklisted SQL in {query_path}")
@@ -457,8 +457,8 @@ def main(
         sql = get_create_object_command(
             schema, table_name, query_path.read_text(), orreplace=replace
         )
-        print(
-            f"Creating {schema}.{table_name} from {'/'.join(query_path.parts[-3:])}",
+        logger.info(
+            f"Creating {schema}.{table_name} from {"/".join(query_path.parts[-3:])}",
             end="... ",
         )
         cnxn.execute(sql)

### 2024-10-23 src/app/utils/elt_config.py
fix inner f string

@@ -458,7 +458,7 @@ def main(
             schema, table_name, query_path.read_text(), orreplace=replace
         )
         logger.info(
-            f"Creating {schema}.{table_name} from {"/".join(query_path.parts[-3:])}",
+            f"Creating {schema}.{table_name} from {'/'.join(query_path.parts[-3:])}",
             end="... ",
         )
         cnxn.execute(sql)

### 2024-10-23 src/utils/get_figures.py
created enum for paper figures

@@ -1,0 +1,104 @@
+from dataclasses import dataclass
+from enum import Enum
+
+
+@dataclass(frozen=True)
+class ProjectFigure:
+    name: str
+    description: str
+    source_url: str = None
+    source_table: str = None
+    current_file: str = None
+
+
+@dataclass(frozen=True)
+class PaperFigure(ProjectFigure):
+    pass
+
+
+@dataclass(frozen=True)
+class PresentationFigure(ProjectFigure):
+    pass
+
+
+class PaperFigures(Enum):
+    ROPE_PDF1 = PaperFigure(
+        "Bayes On One",
+        "A probability density function resulting from a Bayesian Signed Rank Test",
+        current_file="rope_rforest_519_0__etree_358_0_.png",
+    )
+    ROPE_PDF2 = PaperFigure(
+        "Bayes On Two",
+        "A Bayesian posterior plot resulting from a Bayesian hierarchical correlated t-test",
+        current_file="rope_on_two_hxg_boost_531_0__hxg_boost_540_0_.png",
+    )
+    OULAD_COURSE_BREAKDOWN = PaperFigure(
+        "OULAD Course Breakdown",
+        "A breakdown of the OULAD dataset by course modules and domains",
+        current_file="oulad_students_courses.png",
+    )
+    OULAD_ERD = PaperFigure(
+        "OULAD ERD",
+        "An Entity Relationship Diagram of the OULAD dataset",
+        current_file="raw_model.png",
+    )
+    OULAD_VS_2015 = PaperFigure(
+        "OULAD vs 2015",
+        "An evaluation of the similarity between the published OULAD dataset and the 2015 data for CCC module",
+        current_file="oulad_vs_15.png",
+    )
+    OULAD_VS_2015_AGES = PaperFigure(
+        "OULAD vs 2015 Ages",
+        "The distribution of student ages for OULAD data (blue) and 2015 data (red) for CCC module",
+        current_file="oulad_15_age.png",
+    )
+    STUDENT_AGE_BANDS = PaperFigure(
+        "Student Age Bands",
+        "The distribution of student ages in the OULAD dataset",
+        current_file="age_band_by_student.png",
+    )
+    STUDENT_FINAL_RESULTS = PaperFigure(
+        "Student Final Results",
+        "The distribution of final results in the OULAD dataset",
+        current_file="final_result_by_student.png",
+    )
+    STUDENT_REGIONS = PaperFigure(
+        "Student Regions",
+        "The distribution of student regions in the OULAD dataset",
[…]
